### 2013-07-04 proposal.tex
Added start of proposal.

\documentclass{article}

\title{Designing a Unified BBC Search}
\subtitle{Systems Design Coursework Proposal}

\begin{document}

\maketitle

\section{Introduction}

This proposal is for coursework describing the design of a search application
that allows visitors to the BBC website to find anything the BBC offers
online. The focus of the design is likely around the content indexing
systems, which needs to support requirements from all areas of content
production within the BBC so as to acquire all the data required to drive
a search web application.

The scope of the coursework will be restricted to a subset of the content
areas of the BBC website so as to focus on the differing challenges, but
without the designs taking on unnecessary complexity.

\section{The Problem}

Historically, the BBC has grown its presence on the World Wide Web by
allowing individual areas within the organisation to manage their own web
pages independently. This has led to a large variation in the ways
information is stored and how that content is formatted and is accessed.

This historic, technical variation adds to the existing complexity behind
the variation in the nature of the content as the web has matured. Traditional
searches that are optimised for textual items such as news articles might
not work so well for indexing online games aimed at children. Web products
such as iPlayer offer video and audio content with very little accompanying
text.

\end{document}

### 2013-07-04 proposal-contents.tex
First draft of proposal done.

\section{Introduction}

This proposal is for coursework describing the design of a search application
that allows visitors to the BBC website to find anything the BBC offers
online. The focus of the design is likely around the content indexing
systems, which need to support requirements from all areas of content
production.

The scope of the coursework will be restricted to a subset of the content
areas of the BBC website so as to focus on the differing challenges, but
ensure the exercise is concise and free from unnecessary complexity.

\section{The Problem}

Historically, the BBC has grown its presence on the World Wide Web by
allowing individual areas within the organisation to manage their own web
pages independently. This has led to a large variation in the ways
information is stored and how that content is formatted and is accessed.

This historic, technical variation adds to the existing complexity behind
the variation in the nature of the content as the web has matured. Traditional
searches that are optimised for textual items such as news articles might
not work so well for indexing online games aimed at children. Web products
such as iPlayer offer video and audio content with very little accompanying
text.

Website visitors are likely to perceive the BBC website as a single entity
and a unified search can meet those expectations by providing results
across all content areas for any search. There are many
challenges in providing a query interface that can serve varying
mixtures of types of content appropriately for different searches.

There is a dual need to index both a back catalogue of already-published
items and new content as it is written as timely as possible. Some areas
-- such as news -- will require very up-to-the-minute changes as they happen.
This need becomes even stronger for news and sport events that are being
covered live with continuous updates.

Finally, there are areas of content on the BBC website that no longer have
active teams maintaining them. When these areas are just pages lying on
a disk on a server, there is little option other than crawling the live
website to see what is still available.

\section{Proposed System}

The system to be designed is an application with interfaces for sending
and later retrieving content items based on searches given by website users.

The existence of a generic search engine capable of text analysis, indexing
and retrieval can be assumed. Systems that perform these tasks are
already available as free software or proprietary offerings. The bulk of
the problem is in the provision of an application interface that can
accept a large variety of content and interface with content production
workflows with minimal effort required of other teams.

Ultimately, the system needs to focus on the needs for the web application
that will be built to meet users' needs. The requirements
for this front end application are largely speculative and hypothetical
at this stage however.

### 2013-07-04 proposal.tex
First draft of proposal done.

@@
-\documentclass{article}
+\documentclass[10pt,a4paper]{article}
 
-\title{Designing a Unified BBC Search}
-\subtitle{Systems Design Coursework Proposal}
+\usepackage{fullpage}
+
+\title{Designing a Unified BBC Search\\ \vspace{2 mm}{\large Systems Design Coursework Proposal}}
+\author{Ross Fenning}
 
@@
 
-\section{Introduction}
-
-This proposal is for coursework describing the design of a search application
-that allows visitors to the BBC website to find anything the BBC offers
-online. The focus of the design is likely around the content indexing
-systems, which needs to support requirements from all areas of content
-production within the BBC so as to acquire all the data required to drive
-a search web application.
-
-The scope of the coursework will be restricted to a subset of the content
-areas of the BBC website so as to focus on the differing challenges, but
-without the designs taking on unnecessary complexity.
-
-\section{The Problem}
-
-Historically, the BBC has grown its presence on the World Wide Web by
-allowing individual areas within the organisation to manage their own web
-pages independently. This has led to a large variation in the ways
-information is stored and how that content is formatted and is accessed.
-
-This historic, technical variation adds to the existing complexity behind
-the variation in the nature of the content as the web has matured. Traditional
-searches that are optimised for textual items such as news articles might
-not work so well for indexing online games aimed at children. Web products
-such as iPlayer offer video and audio content with very little accompanying
-text.
+\input{proposal-contents}
 

### 2013-08-04 coursework.tex
Added chapter outline to report.

\documentclass{report}
\begin{document}

\chapter{The Problem}

\chapter{Design}

\chapter{Analysis}

\chapter{Evaluation}

\end{document}

### 2013-08-04 coursework.tex
Written some introductory stuff.

@@
 \documentclass{report}
+
+\title{Designing a Search for the BBC}
+
 \begin{document}
@@
 \chapter{The Problem}
+
+\section{Introduction}
+
+The BBC has been publishing content on the World Wide Web since the
+mid 1990s and since then the amount and the diversity has increased
+exponentially. Large websites or indeed the web as a whole would not have
+been usable nor useful without the rise in quality of web search engines to
+help people find content based on keywords or phases that describe or
+appear in the sought after pages.
+
+A large challenge for any web search application is to provide a common
+interface and set of user interactions that can equally index, search
+and link to a diverse range of types of information -- be it in the form
+of text, images, video or games. A more recent challenge has been to
+achieve this in a near-real time way to catch up with the rapid rate at
+which content is added to the web (particulary from microblogging websites
+such as Twitter).
+
+Whilst there are successful general web search engines such a Google that
+will find any piece of content, there is a perceived need for a
+BBC-specific search that makes better use of the internal knowledge the BBC
+has about its own content.
+
+\section{Objectives}
+
+The purpose of this report is to start the high-level design -- and perhaps
+look at the lower levels of one or two aspects -- of a search application
+specific to BBC content. The intent is to provide a consistent user interface
+that allows the audience to find equally news articles, sport results,
+TV catch-up, education resources and everything else the BBC produces.
 

### 2013-08-24 coursework.tex
Added title page, appendix, etc. and ensured the coursework PDF builds.
Added bibliography and sort of finished the first chapter.

@@
-\documentclass{report}
+\documentclass[a4paper]{report}
 
 \title{Designing a Search for the BBC}
+\author{Ross Fenning}
 
@@
 
+\maketitle
+
+\tableofcontents
+
 \chapter{The Problem}
 
-\section{Introduction}
+\section{Rationale}
 
@@
 
+The target audience for the BBC is effectively the entire population of the UK
+and amongst those that do make use of BBC services, there is much diversity
+of needs, preferences and technical ability. It is clear it is no small
+task to design a search-based discovery mechanism of millions of diverse
+pieces of content aimed at millions of diverse people.
+
+A suitable approach for tackling real-word problems is \emph{Soft Systems Methodology} (SSM)
+\cite{checkland2006learning}, which will allows us to stand back from
+an ontological approach of defining what the search system \emph{is} or
+\emph{comprises} and instead take an \emph{epistemological} view of search
+as a system. With this view, we could consider a system that holistically
+transforms members of the public's desires to find online content into
+the consumption of that content -- whether those desires are \emph{precise}
+(e.g. they want an exact article known by headline they saw earlier or a
+particular programme they missed on television) or those desires are
+\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
+materials about the Industrial Revolution).
+
+Checkland \cite{checkland1990soft} decribed a \emph{Rich Picture} approach to
+representing a problem situation early in SSM approaches.
+Given the size and complexity of the
+search system as a whole, a useful initial step is to create such an informal
+representation of what is known about the problem. Figure~\ref{rich-picture}
+shows what I know of the audience, search and most BBC online content areas.
+Note that not all areas are covered and a strong emphasis is placed on TV
+catch-up (e.g. via the iPlayer product). Radio catch-up is not mentioned
+as it shares a lot of similarity with television in terms of use and any
+differences are out of scope for this design.
+
 \chapter{Design}
+
+\section{Use cases}
 
@@
 
+\appendix
+\chapter{Proposal}
+
+\input{proposal-contents}
+
+\bibliographystyle{cell}
+\bibliography{bibtex}
+
 \end{document}

### 2013-08-26 coursework.tex
Created Use Case diagram in Graphviz (PlantUML wasn't doing so well with it).
Made a lot of progress around the main designs. Just about to start talking about AJAX.

@@
 \documentclass[a4paper]{report}
+
+\usepackage{graphicx}
+\usepackage{rotating}
+\usepackage{verbatim}
 
@@
 
-A suitable approach for tackling real-word problems is \emph{Soft Systems Methodology} (SSM)
-\cite{checkland2006learning}, which will allows us to stand back from
+Using \emph{Soft Systems Methodology} (SSM)
+\cite{checkland2006learning}, we can stand back from
 an ontological approach of defining what the search system \emph{is} or
@@
 
+The overall design objective will be to create an initial proposal for a
+search application to drive the missing components within the holistic
+system depicted in figure~\ref{rich-picture}. Some subsystems already
+exist, e.g. for journalists to write news articles and publish them on the
+BBC News website, but for the purposes of this design exercise, we will
+assume no existing application to drive the search and discovery of
+those websites.
+
+It is likely that the design will look to integrate with
+existing subsystems where possible rather than attempt to replicate
+work already done. For example, journalists will prefer that a search
+application can integrate with the system into which they are publishing
+their articles instead of being required to publish their articles into
+two systems.
+
 \chapter{Design}
@@
 \section{Use cases}
+
+From the rich picture in figure~\ref{rich-picture}, we can attempt to
+extract the activities that are clearly within the remit of a search
+application. For example, the ability for editorial staff to manage
+the content of the search indexes sounds like a feature the search
+application would provide. Conversely, television actors and other
+contributors to a programme are likely to interact only within a television
+production subsystem with a producer or content editor being responsible
+for publishing information about the final production's broadcast and
+availability for streaming online.
+
+This is not to say that we can simply cross off certain elements from
+our depiction of the problem because they do not directly interact
+with the subsystem being designed. The \emph{systems thinking} approach
+advocated by Checkland \cite{checkland1999systems} encourages us to
+consider the irreducible properties of each system at each level
+of abstraction. Thus we need to consider not only a search application
+subsystem that solves specific problems for its immediate users, but
+also an application that contributes to the desirable, emergent
+properties of the BBC service as a whole.
+
+In the specific example of television programming, we need to maintain
+systems thinking throughout the design process to ensure that we
+create a search application that both meets the needs of the public
+using the application to search for programmes and forms part of
+a television production and delivery system that itself meets the
+needs of the television-watching public. It is not always the case
+that the holistic system will behave predictably from the behaviours
+of its parts.
+
+Thus a suitable design strategy is to apply systems design to
+the search application in isolation -- as a \emph{hard problem} --
+but then to use the wider system to inform, shape and evaluate that design.
+
+Having extracted the activities that appear to pertain to the
+search application directly (and the actors involved in those activities),
+we can produce a use case UML diagram like that in figure~\ref{use-case}.
+
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{use_case.png}
+  \end{center}
+  \caption{Use case diagram for BBC Search application\label{use-case}}
+\end{sidewaysfigure}
+
+This illustrates only a subset of the expected behaviours for a full
+BBC search application, but touches on some of the diversity of the
+potential uses. For the purposes of our initial design, we can next look
+into defining the system behaviour for some of these use cases.
+
+\section{System Behaviour}
+
+Figure~\ref{sequence-user} shows a sequence diagram defining a user
+interacting with the search system and figure~\ref{sequence-producer}
+shows how a TV producer indirectly interacts with search by providing
+information that ultimately ends up in the search indexes.
+
+\begin{comment}
+@startuml sequence_producer.png
+
+skinparam monochrome true
+
+actor Producer
+participant "Programmes Database" as prog
+participant "Search Index Service" as service
+participant "Search Indexes" as indexes
+
+Producer ->> prog
+
+activate prog
+prog ->> service
+deactivate prog
+
+activate service
+service ->> indexes
+deactivate service
+
+activate indexes
+indexes -> indexes : reindex
+deactivate indexes
+
+@enduml
+\end{comment}
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{sequence_producer.png}
+  \end{center}
+  \caption{Sequence diagram showing publication of programme information to the search indexes\label{sequence-producer}}
+\end{figure}
+
+The key design decision in figure~\ref{sequence-producer} is the use of
+asynchronous messages only. A non-blocking set of interactions such as
+publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
+systems that produce and store progamme information from the search
+application systems. If the systems surrounding the programmes database
+can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
+it to a messaging system, then the search indexes can receive changes to
+information without actors such as TV producers, journalists and content
+editors even being aware this is happening.
+
+\begin{comment}
+@startuml sequence_user.png
+
+skinparam monochrome true
+
+actor User
+participant "BBC Website" as www
+participant "Search Service" as search
+participant "Search Indexes" as indexes
+participant "Source Service" as source
+
+User -> www : types query into search box
+activate www
+
+  www -> search
+  activate search
+
+    note over search
+      The service may want to vary the
+      query for a number of reasons such
+      as the type of device the user has
+      or the nature of the query itself.
+    end note
+
+    search -> search : decide query parameters
+
+    search -> indexes : raw query
+    activate indexes
+    indexes --> search : list of matching items
+    deactivate indexes
+
+    loop for each item
+      search -> source : Fetch more info about item
+      activate source
+
+      note right of search
+        We can enrich the retrieved items with
+        more information from the original source
+        systems rather than replicate all domain
+        knowledge in the search indexes.
+      end note
+
+      source --> search : Returns richer info
+      deactivate source
+    end
+
+  search --> www : list of enriched results
+  deactivate search
+
+www --> User : search results page
+deactivate www
+
+@enduml
+\end{comment}
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{sequence_user.png}
+  \end{center}
+  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
+\end{sidewaysfigure}
+
+Note in figure~\ref{sequence-user} that while the search indexes
+will contain representations of content
+from several source systems, the intention shown is that richer information
+about the domain model will not be held in the search indexes. This goes
+along with the principle of separation of concerns\cite{dijkstra1982role}
+in that the search index component can focus on optimising its data
+structures around retrieval. This kind of modularity also allows source
+systems maintained by other teams to take the responsibility of the
+accuracy of the information, which fits in with the wider holistic view
+of the system in that the volume of information involved requires that
+separate teams are responsible for the accuracy of their data.
+
+This can be seen as similar to the \emph{Lazy Load} pattern
+\cite{fowler2002patterns} in that the search indexes will only return
+stub objects that are capable of retrieving the fuller information
+to need. This, however, could lead to a lot of calls to different
+service applications per page of results. This can be done in parallel, but
+the fact still remains that the user has to wait for all this to
+assemble before seeing even one result.
+
+\section{Domain Model}
+\begin{comment}
+@startuml model.png
+
+skinparam monochrome true
+skinparam circledCharacterRadius 0
+skinparam circledCharacterFontSize 0
+skinparam classFontSize 20
+
+class CreativeWork
+class NewsItem extends CreativeWork
+class Programme extends CreativeWork
+class BlogPost extends CreativeWork
+class LiveCoverage extends CreativeWork
+class LiveEventPage extends CreativeWork
+
+class Thing
+class Person extends Thing
+class Event extends Thing
+class Place extends Thing
+@enduml
+\end{comment}
 

### 2013-08-26 coursework.tex
Done most design. Analysis and evaluation to follow.

@@
 a television production and delivery system that itself meets the
-needs of the television-watching public. It is not always the case
-that the holistic system will behave predictably from the behaviours
-of its parts.
+needs of the television-watching public.
 
@@
 
+This illustrates only a subset of the expected behaviours for a full
+BBC search application, but touches on some of the diversity of the
+potential uses. For the purposes of our initial design, we can next look
+into defining the system behaviour for some of these use cases.
+
 \begin{sidewaysfigure}
@@
 
-This illustrates only a subset of the expected behaviours for a full
-BBC search application, but touches on some of the diversity of the
-potential uses. For the purposes of our initial design, we can next look
-into defining the system behaviour for some of these use cases.
-
 \section{System Behaviour}
-
-Figure~\ref{sequence-user} shows a sequence diagram defining a user
-interacting with the search system and figure~\ref{sequence-producer}
-shows how a TV producer indirectly interacts with search by providing
-information that ultimately ends up in the search indexes.
 
@@
 \end{comment}
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
@@
 \end{figure}
+
+Figure~\ref{sequence-user} shows a sequence diagram defining a user
+interacting with the search system and figure~\ref{sequence-producer}
+shows how a TV producer indirectly interacts with search by providing
+information that ultimately ends up in the search indexes.
 
@@
 \end{comment}
-\begin{sidewaysfigure}
+\begin{figure}[p]
   \begin{center}
@@
   \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
-\end{sidewaysfigure}
+\end{figure}
 
@@
 
+One solution to this in modern web application design is to
+push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
+Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
+this still requires just as many calls to backend services --
+perhaps even more complexity as the calls are going through
+more layers -- it can give a user experience than appears more responsive.
+
+Preparing a search results page with minimal information that is then
+augmented asynchronously is a user experience technique that gives the
+illusion of lower latency; the additional information can update the page
+during the user's reaction time in the best case. This is an important
+aspect of user experience to get right as multivariate testing at Google
+in 2006 showed that an additional 500ms of latency dropped traffic
+and revenue by 20\%. \cite{linden2006marissa}
+
+\begin{comment}
+@startuml sequence_ajax.png
+
+skinparam monochrome true
+
+actor User
+participant "BBC Website" as www
+participant "Search Service" as search
+participant "Search Indexes" as indexes
+participant "Source Service" as source
+
+User -> www : types query into search box
+activate www
+
+  www -> search
+  activate search
+
+    note over search
+      The service may want to vary the
+      query for a number of reasons such
+      as the type of device the user has
+      or the nature of the query itself.
+    end note
+
+    search -> search : decide query parameters
+
+    search -> indexes : raw query
+    activate indexes
+    indexes --> search : list of matching items
+    deactivate indexes
+
+    search --> www : Return stub items
+    deactivate search
+
+    www --> User : search results page
+
+    note over www
+      Website remains active using Javascript to do 
+      AJAX requests for further information for
+      each result.
+    end note
+
+    loop for each item
+      www ->> search : Fetch more info about item
+      activate search
+      search -> source : Proxy to source for info
+      activate source
+      source --> search : Return info in source's own format
+      deactivate source
+      search --> www : Return info in common format
+      deactivate search
+      www --> User : Update page in front of user as info arrives
+    end
+
+deactivate www
+
+@enduml
+\end{comment}
+\begin{figure}[p]
+  \begin{center}
+    \includegraphics[width=\linewidth]{sequence_ajax.png}
+  \end{center}
+  \caption{Sequence diagram showing rich information lazy-loaded via AJAX\label{sequence-ajax}}
+\end{figure}
+
 \section{Domain Model}
+
+It has been expressed already that a BBC-wide search application
+is going to have to index, retrieve and display a diverse set of
+information. Parts of the application might well want to incorporate
+a domain model \cite{fowler2002patterns} so as to understand how
+to perform each of these actions against each possible item
+the search application could return as a search result. A maximal
+model is shown in figure~\ref{model} that attempts to capture
+a good proportion of the content and concepts the BBC has
+been attempting to model over several years. This model is
+an aggregate of individual ontologies developed for specific purposes,
+but given the search application has to provide the discovery for
+the full set of this information, it is not unreasonable that
+a search application would have a domain model that covers the totality.
+
+Note that complexity of information for programmes alone. \cite{raimond2009bbc}
+A programme to a member of the public could actually refer to an
+exact episode or indeed the \emph{brand}, i.e. the title that
+persists to all episodes. An example of a brand would be
+\emph{Doctor Who}, which itself contains multiple series, which in turn
+contain a collection of episodes. Note that the brand itself has episodes
+as immediate children that do not live under a series, e.g. Christmas specials.
+It is also the case that certain things do not have brands or series, e.g.
+a film is modelled as a one-off episode.
+
+This leads to some difficult questions for a search application. If a user
+searches for the text ``doctor who'', are they expecting a link to the
+latest episode to watch on iPlayer, information about the next episode
+-- such as when it is due to be broadcast -- or a link to the overall
+home page for the entire Doctor Who brand?
+
+The model also skims the surface of the sport ontology \cite{rayfield2011bbc}
+created before the 2012 Olympic games, which aims to model the whole domain
+of sporting personalities, events and competitions (and more). This might
+be too fine-grained for the domain model used within the search application,
+but it is likely that people will want to search for competitions like
+``World Cup'' or sporting disciplines such as ``football''. A search application
+that understands these concepts as entities in their own right may well
+be able to direct users at a curated, dedicated ``home page'' thereof alongside
+simply matching articles and other works that contain those terms only.
+
 \begin{comment}
@@
 skinparam circledCharacterFontSize 0
-skinparam classFontSize 20
 
-class CreativeWork
+package CreativeWorks {
+class CreativeWork {
+  title : String
+  dateModified : DateTime
+  dateCreated : DateTime
+  category : String
+  description : String
+  thumbnail: Image
+}
 class NewsItem extends CreativeWork
-class Programme extends CreativeWork
 class BlogPost extends CreativeWork
@@
 
-class Thing
+interface Format
+class TextualFormat extends Format
+class VideoFormat extends Format
+class InteractiveFormat extends Format
+class ImageFormat extends Format
+class AudioFormat extends Format
+class PictureGalleryFormat extends Format
+}
+
+package Programmes {
+class Programme
+Programme <|-r- CreativeWork
+class Brand extends Programme
+class Series extends Programme
+class Episode extends Programme
+
+class Service
+class Version
+class Broadcast
+class Ondemand
+}
+
+Service "1" -- "0..n" Programme : masterBrand
+Episode "1" *-- "0..n" Version : hasVersions
+
+Version "1" -- "0..n" Broadcast : broadcasts
+Version "1" -- "0..n" Ondemand : availableOndemandWindows
+
+Broadcast "1..n" -- "1" Service : broadcastOn
+Ondemand "1..n" -- "1" Service : availableOn
+
+Brand "1" *-r- "0..n" Series
+Series "1" *-d- "0..n" Series
+Series "1" *-r- "0..n" Episode
+
+package Concepts {
+class WebDocument
+class Thing {
+  preferredLabel
+}
 class Person extends Thing
@@
 class Place extends Thing
+class Theme extends Thing
+class Organisation extends Thing
+}
+
+CreativeWork "1" -- "1..2" WebDocument : primaryContent
+Thing "1" -- "0..n" WebDocument : primaryTopic
+CreativeWork "0..n" -- "1" Format : primaryFormat
+CreativeWork "0..n" -- "0..n" Thing : tag
+Thing "0..n" -- "0..n" Thing : notablyAssociatedWith
+
+package Sport {
+class SportCompetition extends Event
+class SportDiscipline extends Thing
+}
+
+Event "0..n" -- "0..n" Programme : coverage
+SportCompetition "0..n" -- "0..n" Person : competesIn
+SportDiscipline "1" -- "0..n" SportCompetition
+
 @enduml
 \end{comment}
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{model.png}
+  \end{center}
+  \caption{Domain model for content items and other things pertinent to BBC contenet\label{model}}
+\end{sidewaysfigure}
 
 \chapter{Analysis}
+\label{analysis}
 

### 2013-08-28 coursework.tex
Fixed typo.
Very close to a first draft. Need to round off the evaluation and do some of the reshuffling of e.g. the first para of the design chapter then do a formal review.

@@
 
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{rich-picture.png}
+  \end{center}
+  \caption{Rich Picture of the BBC search system\label{rich-picture}}
+\end{sidewaysfigure}
+
 \chapter{Design}
+\label{design}
 
@@
 
-Figure~\ref{sequence-user} shows a sequence diagram defining a user
-interacting with the search system and figure~\ref{sequence-producer}
-shows how a TV producer indirectly interacts with search by providing
-information that ultimately ends up in the search indexes.
-
-The key design decision in figure~\ref{sequence-producer} is the use of
-asynchronous messages only. A non-blocking set of interactions such as
-publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
-systems that produce and store progamme information from the search
-application systems. If the systems surrounding the programmes database
-can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
-it to a messaging system, then the search indexes can receive changes to
-information without actors such as TV producers, journalists and content
-editors even being aware this is happening.
-
 \begin{comment}
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{sequence_user.png}
+    \includegraphics[height=0.4\textheight]{sequence_user.png}
   \end{center}
@@
 \end{figure}
-
-Note in figure~\ref{sequence-user} that while the search indexes
-will contain representations of content
-from several source systems, the intention shown is that richer information
-about the domain model will not be held in the search indexes. This goes
-along with the principle of separation of concerns\cite{dijkstra1982role}
-in that the search index component can focus on optimising its data
-structures around retrieval. This kind of modularity also allows source
-systems maintained by other teams to take the responsibility of the
-accuracy of the information, which fits in with the wider holistic view
-of the system in that the volume of information involved requires that
-separate teams are responsible for the accuracy of their data.
-
-This can be seen as similar to the \emph{Lazy Load} pattern
-\cite{fowler2002patterns} in that the search indexes will only return
-stub objects that are capable of retrieving the fuller information
-to need. This, however, could lead to a lot of calls to different
-service applications per page of results. This can be done in parallel, but
-the fact still remains that the user has to wait for all this to
-assemble before seeing even one result.
-
-One solution to this in modern web application design is to
-push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
-Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
-this still requires just as many calls to backend services --
-perhaps even more complexity as the calls are going through
-more layers -- it can give a user experience than appears more responsive.
-
-Preparing a search results page with minimal information that is then
-augmented asynchronously is a user experience technique that gives the
-illusion of lower latency; the additional information can update the page
-during the user's reaction time in the best case. This is an important
-aspect of user experience to get right as multivariate testing at Google
-in 2006 showed that an additional 500ms of latency dropped traffic
-and revenue by 20\%. \cite{linden2006marissa}
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{sequence_ajax.png}
+    \includegraphics[height=0.4\textheight]{sequence_ajax.png}
   \end{center}
@@
 \end{figure}
+
+Figure~\ref{sequence-user} shows a sequence diagram defining a user
+interacting with the search system and figure~\ref{sequence-producer}
+shows how a TV producer indirectly interacts with search by providing
+information that ultimately ends up in the search indexes.
+
+The key design decision in figure~\ref{sequence-producer} is the use of
+asynchronous messages only. A non-blocking set of interactions such as
+publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
+systems that produce and store progamme information from the search
+application systems. If the systems surrounding the programmes database
+can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
+it to a messaging system, then the search indexes can receive changes to
+information without actors such as TV producers, journalists and content
+editors even being aware this is happening.
+
+Note in figure~\ref{sequence-user} that while the search indexes
+will contain representations of content
+from several source systems, the intention shown is that richer information
+about the domain model will not be held in the search indexes. This goes
+along with the principle of separation of concerns\cite{dijkstra1982role}
+in that the search index component can focus on optimising its data
+structures around retrieval. This kind of modularity also allows source
+systems maintained by other teams to take the responsibility of the
+accuracy of the information, which fits in with the wider holistic view
+of the system in that the volume of information involved requires that
+separate teams are responsible for the accuracy of their data.
+
+This can be seen as similar to the \emph{Lazy Load} pattern
+\cite{fowler2002patterns} in that the search indexes will only return
+stub objects that are capable of retrieving the fuller information
+to need. This, however, could lead to a lot of calls to different
+service applications per page of results. This can be done in parallel, but
+the fact still remains that the user has to wait for all this to
+assemble before seeing even one result.
+
+One solution to this in modern web application design is to
+push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
+Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
+this still requires just as many calls to backend services --
+perhaps even more complexity as the calls are going through
+more layers -- it can give a user experience than appears more responsive.
+
+Preparing a search results page with minimal information that is then
+augmented asynchronously is a user experience technique that gives the
+illusion of lower latency; the additional information can update the page
+during the user's reaction time in the best case. This is an important
+aspect of user experience to get right as multivariate testing at Google
+in 2006 showed that an additional 500ms of latency dropped traffic
+and revenue by 20\%. \cite{linden2006marissa}
 
@@
 class Programme
-Programme <|-r- CreativeWork
+Programme -r-|> CreativeWork
 class Brand extends Programme
@@
   \end{center}
-  \caption{Domain model for content items and other things pertinent to BBC contenet\label{model}}
+  \caption{Domain model for content items and other things pertinent to BBC content\label{model}}
 \end{sidewaysfigure}
 
-\chapter{Analysis}
-\label{analysis}
+\section{Discussion and Appraisal}
+\label{appraisal}
+
+The first question that should be asked is whether the problem
+given has been solved as much as it can be. The problem of
+a BBC-wide search application was predicted  --
+and has certainly shown itself -- to be a very large-scale problem, the
+full extent of which cannot be covered in this report. Thus it
+is reasonable to conclude that the problem is not yet solved
+at every level, but the high-level solutions are certainly promising.
+
+The use case diagram is likely not complete and would need
+a significant amount of user research and requirements-gathering
+to collection all the possible use cases of the search system. It
+is likely that the variations of the use cases are so numerous
+that different diagrams exploring different combinations of use
+cases should be made to replace the single one given. For instance,
+very little has been touched on around user's seeking educational
+and informative material such as GCSE Bitesize or any other
+learning resouces.
+
+The sequence diagram for the producer (or any other content creator)
+indirectly getting their content into the seach system demonsrates
+the need for asynchronous messaging (and publish-subscribe), but
+the nuances of such a process are not comphrehensively shown in
+this format. A better illutration for such a message-based integration
+system might be derived from the illutrated patterns created
+by Hohpe and Woolf. \cite{hohpe2004enterprise}
+
+The behaviour of the query web application in figure~\ref{sequence-user}
+is defined with a hard line
+taken on keeping the information stored in the indexes to a minimum.
+At a basic level, this is not unlike a \emph{content enricher} pattern
+\cite{hohpe2004enterprise} whereby the search application
+business layer enriches the stubs in the indexes with information
+the source system (the index) simply does not have. At a more purist
+extreme, this could follow a \emph{claim check} pattern where
+the index returns only globally-unique identifiers for the matching
+items and makes no attempt to present any other knowledge about them
+(and thus avoids any synchronisation issues if an item is updated as
+source).
+
+The latter approach fully decouples the search indexes from any
+deeper information -- leaving that responsbility to appropriate
+source system -- but means that the raw, stub results are near useful
+to an end user. This makes the AJAX-based alternative approach
+in figure~\ref{sequence-ajax}
+less of a desirable option (would a user really be presented a list
+of URIs while some Javascript code replaces them one by one with
+actual information?). Given the AJAX-driven behaviour appears
+desirable in terms of responsiveness, it would seem that some trade-off
+would need to happen in terms of what the indexes store as additional
+information.
+
+These decisions relate to how the system would implement the data model
+in figure~\ref{model}. The onotology described is an aggregation
+of several efforts by Raimond \cite{raimond2009bbc}, Rayfield
+\cite{rayfield2011bbc} and others -- along with some additional work
+to join them together -- to represent the wealth of
+information with which the BBC deals. It could be argued both that
+a search application that \emph{understands} this diversity of
+content must reflect it in its domain model but that a search
+application that is \emph{coupled} to the individual ontologies
+in this way is brittle with regard to changes therein. Duplication
+would only harm maintainability.
+
+Thus the domain model given in figure~\ref{model} should only serve
+as a communication artefact that leads to further development of
+a domain model more suitable to the needs of the search application
+without the need to maintain more than is necessary. The use
+of \emph{subtype polymorphism} \cite{booch2007object} is likely
+to be key to ensure the search domain model needs only use the APIs
+it needs. For example, does the search application have a need
+to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
+for the purposes of displaying the search result's title? If the
+CreativeWork top-level class has a title property, then the domain
+model so far to enable that one behaviour needs only one class!
+
+The application could go further and interact via a single
+SearchResult \emph{facade} \cite{fowler2002patterns} whose
+instances provide appropriate responses to canonical hooks
+such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
+via polymorphic \emph{composition} with different target classes
+from the fuller domain model. Given that the search indexes
+are likely to take in content from any number of future systems,
+there is an appeal to taking a schemaless approach \cite{sadalage2012nosql}
+and allow the search application's view layer to display
+different kinds of results differently via \emph{duck typing}.
+\cite{python2013ducktyping}
+
+A dynamic, schema-free domain model used within the search application
+-- noting that, of course, schemaless truly means there is an
+implicit schema in the logic that creates these dynamic objects from
+source systems \cite{sadalage2012nosql} -- could prove to aid the
+search system's need to model different kinds of data in the same
+index. For example, our designers might express a desire to put
+small summaries of weather forecasts within search results that
+contain places. In the static sense, we could say that anything
+of \emph{Place} type is displayed with such a feature. With
+a dynamic, duck-typed model, we could ask
+``does this item have weather?'' in place of ``is this a place?'', thus
+allowing for the future design that extends forecasts to football
+matches (since football matches are \emph{Event}s that occur in
+a \emph{Place}, it is reasonable for a weather property to be
+set thereon).
+
+Some of the advantages from duck-typing could be mirrored in
+providing building the domain model around interfaces -- e.g.
+\emph{class FootballMatch extends Event implements WeatherLocation} --
+but it is still cumbersome to create such a large, static-typed
+domain model that is used both at index time (in extracting the
+information to build the indexes) and at query time (to understand
+what item we have found and how to present it to the user).
+
+Overall, we have some promising, high-level models from which to
+start making such more fine-grained decisions about the search
+application. The use cases are likely sufficient for early iterations
+or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
+the behaviours capture the overall needs of the system. There is still
+much scope for returning to our systems thinking and Soft Systems
+Methodology to monitor the general model for Checkland's ``3 Es''
+(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
+which is only briefly touched on in my attempts to relate the
+data model to the user's interaction with the system.
 
 \chapter{Evaluation}
+\ref{evaluation}
+
+Overall, we have some promising, high-level models from which to
+start making such more fine-grained decisions about the search
+application. The use cases are likely sufficient for early iterations
+or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
+the behaviours capture the overall needs of the system. There is still
+much scope for returning to our systems thinking and Soft Systems
+Methodology to monitor the general model for Checkland's ``3 Es''
+(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
+which is only briefly touched on in my attempts to relate the
+data model to the user's interaction with the system.
+
+The high-level nature of the modelling achieved has made it
+difficult to meet any objectives over performance, latency or
+robustness of software components involved. A BBC search application
+needs to index news as it is published, serve millions of unique
+visits every week and minimise potential for losing information. These
+non-functional requirements are a challenge in their own right
+and have not been met with the UML modelling presented.
+
+This is not to say that UML is not capable as a tool for presenting
+architecture around performance and resilience. It is perhaps
+more appropriate to model and present some of these aspects through
+component and deployment diagrams. Behaviour diagrams such as sequence
+and activity do not suit well to showing timing or performance, although
+a series of sequence diagrams could show how behaviour changes
+in parts of the system to tolerate failure of certain components (e.g.
+one component could be modelled to return from an internal cache if
+a collaborator is returning temporary error status codes).
+
+Even the models that are presented in this report do not paint the full
+picture, but it could be argued that it is not their purpose to do so.
+As stated at the end of section~\ref{appraisal}, the use case diagram
+provides a starting point that might be sufficient for an early
+iteration of a project in an \emph{Agile} methodology. \cite{beck2001manifesto}
+
+An Agile approach to developing the search application could distill
+the use cases even further and shape the requirements to the rest
+thereof later in the development process based on feedback and reacting
+to changes. A similar approach would allow us to start with the smaller
+domain model also discussed in section~\ref{appraisal} and allow it to grow
+to the necessary size to need -- i.e. we can defer the decision of ``how big
+should the domain model be?'' until we are at a point where we have more
+information to answer that (at which point we would hope it is as comprehensive
+as is necessary to support the application currently running and no more).
+
+Thus even if the use case and domain models are not as comprehensive or
+as honed as they need to be to build the entire application, they serve
+their purpose adequately to communicate the first iterations of
+development or -- especially in the case of the domain model -- information
+pertaining to the whole organisation, even if only small parts of it are
+they modelled directly in the application being built.
+
+The sequence diagrams seemed to provoke more debate of the merits of
+returning rich information in a single response versus an AJAX-driven
+approach (or some trade-off in between). Again, I would emphasise the
+communication aspect UML modelling and argue that encouraging such debate
+is a successful application of UML, not a failure because a decision
+has not been made between two designs at this early stage.
+
+Some of this hints at drawback of UML modelling being that it encourages
+a lot of design decision at an early stage -- stage at which we arguably
+have the least information. \cite{kelly2013conway} There are plenty of
+efforts in spite of this that promote modelling and UML being used
+compatibly within an Agile process. The use of other modelling techniques
+in an Agile setting such as
+Rational Unified Process (RUP) and Agile Unified Process (AUP) are described by
+Ambler. \cite{ambler2002agile} It may have been more suitable to incorporate
+a more diverse range of modelling techniques in the design and analysis
+presented so as to find the true strengths of each respective approach.
 

### 2013-08-28 coursework.tex
Added concluding paragraph, which makes this a candidate first draft. Also added makefile.

@@
 \begin{comment}
-@startuml sequence_producer.png
+@startuml plant_sequence_producer.png
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{sequence_producer.png}
+    \includegraphics[width=\linewidth]{plant_sequence_producer.png}
   \end{center}
@@
 \begin{comment}
-@startuml sequence_user.png
+@startuml plant_sequence_user.png
 
@@
   \begin{center}
-    \includegraphics[height=0.4\textheight]{sequence_user.png}
+    \includegraphics[height=0.4\textheight]{plant_sequence_user.png}
   \end{center}
@@
 \begin{comment}
-@startuml sequence_ajax.png
+@startuml plant_sequence_ajax.png
 
@@
   \begin{center}
-    \includegraphics[height=0.4\textheight]{sequence_ajax.png}
+    \includegraphics[height=0.4\textheight]{plant_sequence_ajax.png}
   \end{center}
@@
 \begin{comment}
-@startuml model.png
+@startuml plant_model.png
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{model.png}
+    \includegraphics[width=\linewidth]{plant_model.png}
   \end{center}
@@
 \chapter{Evaluation}
-\ref{evaluation}
+\label{evaluation}
 
@@
 provides a starting point that might be sufficient for an early
-iteration of a project in an \emph{Agile} methodology. \cite{beck2001manifesto}
+iteration of a project in an \emph{Agile} methodology. \cite{beck2001agile}
 
@@
 
-Some of this hints at drawback of UML modelling being that it encourages
-a lot of design decision at an early stage -- stage at which we arguably
-have the least information. \cite{kelly2013conway} There are plenty of
+Some of this hints at a drawback of UML modelling being that it encourages
+a lot of design decision at an early stage of a project -- a stage at which we arguably
+have the least information. \cite{kelly2013conway} However, there are plenty of
 efforts in spite of this that promote modelling and UML being used
@@
 presented so as to find the true strengths of each respective approach.
+
+In conclusion, the UML modelling presented is a key part of solving
+the BBC search problem, but it is far from sufficient in its own right.
+Designing to the level of detail required would result in a rigid
+development plan that made unverified assumptions, but an iterative
+approach to modelling that starts at a high-level and updates as
+development progresses could be used successfully in such a project.
 

### 2013-08-29 coursework.tex
Did some amendments following proof read.

@@
 
-\section{Rationale}
+\section{Background}
 
@@
 mid 1990s and since then the amount and the diversity has increased
-exponentially. Large websites or indeed the web as a whole would not have
-been usable nor useful without the rise in quality of web search engines to
-help people find content based on keywords or phases that describe or
-appear in the sought after pages.
+exponentially. Large websites -- or indeed the web as a whole --
+would not have been usable nor useful without the rise in quality of
+web search engines.
 
@@
 specific to BBC content. The intent is to provide a consistent user interface
-that allows the audience to find equally news articles, sport results,
+that allows the audience to find news articles, sport results,
 TV catch-up, education resources and everything else the BBC produces.
@@
 
-Checkland \cite{checkland1990soft} decribed a \emph{Rich Picture} approach to
-representing a problem situation early in SSM approaches.
+Checkland and Scoles \cite{checkland1990soft} decribed a \emph{Rich Picture} approach
+for representing a problem situation early in SSM approaches.
 Given the size and complexity of the
@@
 BBC News website, but for the purposes of this design exercise, we will
-assume no existing application to drive the search and discovery of
+assume no existing application to drive a search-based discovery of
 those websites.
@@
 cases should be made to replace the single one given. For instance,
-very little has been touched on around user's seeking educational
+very little has been touched on around users seeking educational
 and informative material such as GCSE Bitesize or any other

### 2013-08-29 coursework.tex
Finished applying changes from proof read.

@@
 \usepackage{verbatim}
+\usepackage{url}
 
@@
 search application directly (and the actors involved in those activities),
-we can produce a use case UML diagram like that in figure~\ref{use-case}.
+we can produce the use case UML diagram shown in figure~\ref{use-case}.
 
@@
 
-Figure~\ref{sequence-user} shows a sequence diagram defining a user
-interacting with the search system and figure~\ref{sequence-producer}
+Figure~\ref{sequence-producer}
 shows how a TV producer indirectly interacts with search by providing
-information that ultimately ends up in the search indexes.
+information that ultimately ends up in the search indexes and
+figure~\ref{sequence-user} shows a sequence diagram defining a user
+interacting with the search system
 
@@
 it to a messaging system, then the search indexes can receive changes to
-information without actors such as TV producers, journalists and content
-editors even being aware this is happening.
+information without TV producers, journalists, content
+editors, etc. even being aware this is happening.
 
@@
 about the domain model will not be held in the search indexes. This goes
-along with the principle of separation of concerns\cite{dijkstra1982role}
+along with the principle of separation of concerns \cite{dijkstra1982role}
 in that the search index component can focus on optimising its data
@@
 accuracy of the information, which fits in with the wider holistic view
-of the system in that the volume of information involved requires that
+of the system: the volume of information involved requires that
 separate teams are responsible for the accuracy of their data.
@@
 perhaps even more complexity as the calls are going through
-more layers -- it can give a user experience than appears more responsive.
+more layers -- it can give a user experience that appears more responsive.
 
@@
 illusion of lower latency; the additional information can update the page
-during the user's reaction time in the best case. This is an important
-aspect of user experience to get right as multivariate testing at Google
-in 2006 showed that an additional 500ms of latency dropped traffic
-and revenue by 20\%. \cite{linden2006marissa}
+during the user's reaction time in the best case.
 
@@
 A programme to a member of the public could actually refer to an
-exact episode or indeed the \emph{brand}, i.e. the title that
-persists to all episodes. An example of a brand would be
+exact episode or indeed the \emph{brand}, i.e. the title of the programme
+in general. An example of a brand would be
 \emph{Doctor Who}, which itself contains multiple series, which in turn
@@
 be able to direct users at a curated, dedicated ``home page'' thereof alongside
-simply matching articles and other works that contain those terms only.
+simply matching articles and other works that contain those terms.
 
@@
 
-\section{Discussion and Appraisal}
+\section{Discussion and Analysis}
 \label{appraisal}
 
-The first question that should be asked is whether the problem
-given has been solved as much as it can be. The problem of
+xThe problem of
 a BBC-wide search application was predicted --
@@
 The sequence diagram for the producer (or any other content creator)
-indirectly getting their content into the seach system demonsrates
+indirectly getting their content into the search system demonsrates
 the need for asynchronous messaging (and publish-subscribe), but
-the nuances of such a process are not comphrehensively shown in
+the nuances of such a process are not comprehensively shown in
 this format. A better illutration for such a message-based integration
@@
 items and makes no attempt to present any other knowledge about them
-(and thus avoids any synchronisation issues if an item is updated as
+(and thus avoids any synchronisation issues if an item is updated at
 source).
 
-The latter approach fully decouples the search indexes from any
+The latter pattern fully decouples the search indexes from any
 deeper information -- leaving that responsbility to appropriate
-source system -- but means that the raw, stub results are near useful
+source system -- but means that the raw, stub results are near-useless
 to an end user. This makes the AJAX-based alternative approach
@@
 of URIs while some Javascript code replaces them one by one with
-actual information?). Given the AJAX-driven behaviour appears
+actual information?). Given the AJAX-driven behaviour still appears
 desirable in terms of responsiveness, it would seem that some trade-off
@@
 a domain model more suitable to the needs of the search application
-without the need to maintain more than is necessary. The use
+without the burden of maintaining more than is necessary. The use
 of \emph{subtype polymorphism} \cite{booch2007object} is likely
-to be key to ensure the search domain model needs only use the APIs
+to be key to ensure the search domain model contains only the APIs
 it needs. For example, does the search application have a need
@@
 
-Some of the advantages from duck-typing could be mirrored in
-providing building the domain model around interfaces -- e.g.
-\emph{class FootballMatch extends Event implements WeatherLocation} --
-but it is still cumbersome to create such a large, static-typed
-domain model that is used both at index time (in extracting the
-information to build the indexes) and at query time (to understand
-what item we have found and how to present it to the user).
-
 Overall, we have some promising, high-level models from which to
@@
 
-Overall, we have some promising, high-level models from which to
-start making such more fine-grained decisions about the search
-application. The use cases are likely sufficient for early iterations
-or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
-the behaviours capture the overall needs of the system. There is still
-much scope for returning to our systems thinking and Soft Systems
-Methodology to monitor the general model for Checkland's ``3 Es''
-(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
-which is only briefly touched on in my attempts to relate the
-data model to the user's interaction with the system.
-
 The high-level nature of the modelling achieved has made it
@@
 This is not to say that UML is not capable as a tool for presenting
-architecture around performance and resilience. It is perhaps
+architecture around performance and resilience. However, it is perhaps
 more appropriate to model and present some of these aspects through
@@
 a series of sequence diagrams could show how behaviour changes
-in parts of the system to tolerate failure of certain components (e.g.
+in parts of the system to tolerate failure of other components (e.g.
 one component could be modelled to return from an internal cache if
@@
 should the domain model be?'' until we are at a point where we have more
-information to answer that (at which point we would hope it is as comprehensive
-as is necessary to support the application currently running and no more).
+information to answer such a question.
 
@@
 approach (or some trade-off in between). Again, I would emphasise the
-communication aspect UML modelling and argue that encouraging such debate
+communication aspect of UML modelling and argue that encouraging such debate
 is a successful application of UML, not a failure because a decision
@@
 in an Agile setting such as
-Rational Unified Process (RUP) and Agile Unified Process (AUP) are described by
-Ambler. \cite{ambler2002agile} It may have been more suitable to incorporate
+Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
+suggested as suitable in an Agile project.
+\cite{ambler2002agile} It may have been more suitable to incorporate
 a more diverse range of modelling techniques in the design and analysis

### 2014-02-05 paper.tex
Renamed coursework file to paper.

--- 2013-08-29 coursework.tex
@@
 \usepackage{url}
+\usepackage[square]{natbib}
 
@@
 Using \emph{Soft Systems Methodology} (SSM)
-\cite{checkland2006learning}, we can stand back from
+\citep{checkland2006learning}, we can stand back from
 an ontological approach of defining what the search system \emph{is} or
@@
 
-Checkland and Scoles \cite{checkland1990soft} decribed a \emph{Rich Picture} approach
+Checkland and Scoles \citep{checkland1990soft} decribed a \emph{Rich Picture} approach
 for representing a problem situation early in SSM approaches.
@@
 with the subsystem being designed. The \emph{systems thinking} approach
-advocated by Checkland \cite{checkland1999systems} encourages us to
+advocated by Checkland \citep{checkland1999systems} encourages us to
 consider the irreducible properties of each system at each level
@@
 asynchronous messages only. A non-blocking set of interactions such as
-publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
+publish-subscribe \citep{hohpe2004enterprise} is a good way to decouple
 systems that produce and store progamme information from the search
 application systems. If the systems surrounding the programmes database
-can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
+can be built a \emph{channel adapter} \citep{hohpe2004enterprise} to integrate
 it to a messaging system, then the search indexes can receive changes to
@@
 about the domain model will not be held in the search indexes. This goes
-along with the principle of separation of concerns \cite{dijkstra1982role}
+along with the principle of separation of concerns \citep{dijkstra1982role}
 in that the search index component can focus on optimising its data
@@
 This can be seen as similar to the \emph{Lazy Load} pattern
-\cite{fowler2002patterns} in that the search indexes will only return
+\citep{fowler2002patterns} in that the search indexes will only return
 stub objects that are capable of retrieving the fuller information
@@
 One solution to this in modern web application design is to
-push the lazy loading into the web browser using AJAX. \cite{garrett2005ajax}
+push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
 Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
@@
 information. Parts of the application might well want to incorporate
-a domain model \cite{fowler2002patterns} so as to understand how
+a domain model \citep{fowler2002patterns} so as to understand how
 to perform each of these actions against each possible item
@@
 
-Note that complexity of information for programmes alone. \cite{raimond2009bbc}
+Note that complexity of information for programmes alone. \citep{raimond2009bbc}
 A programme to a member of the public could actually refer to an
@@
 
-The model also skims the surface of the sport ontology \cite{rayfield2011bbc}
+The model also skims the surface of the sport ontology \citep{rayfield2011bbc}
 created before the 2012 Olympic games, which aims to model the whole domain
@@
 system might be derived from the illutrated patterns created
-by Hohpe and Woolf. \cite{hohpe2004enterprise}
+by Hohpe and Woolf. \citep{hohpe2004enterprise}
 
@@
 At a basic level, this is not unlike a \emph{content enricher} pattern
-\cite{hohpe2004enterprise} whereby the search application
+\citep{hohpe2004enterprise} whereby the search application
 business layer enriches the stubs in the indexes with information
@@
 in figure~\ref{model}. The onotology described is an aggregation
-of several efforts by Raimond \cite{raimond2009bbc}, Rayfield
-\cite{rayfield2011bbc} and others -- along with some additional work
+of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
+\citep{rayfield2011bbc} and others -- along with some additional work
 to join them together -- to represent the wealth of
@@
 without the burden of maintaining more than is necessary. The use
-of \emph{subtype polymorphism} \cite{booch2007object} is likely
+of \emph{subtype polymorphism} \citep{booch2007object} is likely
 to be key to ensure the search domain model contains only the APIs
@@
 The application could go further and interact via a single
-SearchResult \emph{facade} \cite{fowler2002patterns} whose
+SearchResult \emph{facade} \citep{fowler2002patterns} whose
 instances provide appropriate responses to canonical hooks
@@
 are likely to take in content from any number of future systems,
-there is an appeal to taking a schemaless approach \cite{sadalage2012nosql}
+there is an appeal to taking a schemaless approach \citep{sadalage2012nosql}
 and allow the search application's view layer to display
 different kinds of results differently via \emph{duck typing}.
-\cite{python2013ducktyping}
+\citep{python2013ducktyping}
 
@@
 implicit schema in the logic that creates these dynamic objects from
-source systems \cite{sadalage2012nosql} -- could prove to aid the
+source systems \citep{sadalage2012nosql} -- could prove to aid the
 search system's need to model different kinds of data in the same
@@
 application. The use cases are likely sufficient for early iterations
-or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
+or a \emph{Minimal Viable Product} \citep{junk2000dynamic} and
 the behaviours capture the overall needs of the system. There is still
@@
 Methodology to monitor the general model for Checkland's ``3 Es''
-(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
+(efficacy, efficiency and effectiveness) \citep{checkland1990soft},
 which is only briefly touched on in my attempts to relate the
@@
 provides a starting point that might be sufficient for an early
-iteration of a project in an \emph{Agile} methodology. \cite{beck2001agile}
+iteration of a project in an \emph{Agile} methodology. \citep{beck2001agile}
 
@@
 a lot of design decision at an early stage of a project -- a stage at which we arguably
-have the least information. \cite{kelly2013conway} However, there are plenty of
+have the least information. \citep{kelly2013conway} However, there are plenty of
 efforts in spite of this that promote modelling and UML being used
@@
 suggested as suitable in an Agile project.
-\cite{ambler2002agile} It may have been more suitable to incorporate
+\citep{ambler2002agile} It may have been more suitable to incorporate
 a more diverse range of modelling techniques in the design and analysis

### 2014-02-05 paper.tex
Moved into Springer format and fixed makefile as citations stopped working.

@@
-\documentclass[a4paper]{report}
+\documentclass{llncs}
 
@@
 \author{Ross Fenning}
+\institute{BBC}
 
@@
 
-\chapter{The Problem}
+\section{The Problem}
 
-\section{Background}
+\subsection{Background}
 
@@
 
-\section{Objectives}
+\subsection{Objectives}
 
@@
 
-\chapter{Design}
+\section{Design}
 \label{design}
 
-\section{Use cases}
+\subsection{Use cases}
 
@@
 
-\section{System Behaviour}
+\subsection{System Behaviour}
 
@@
 
-\section{Domain Model}
+\subsection{Domain Model}
 
@@
 
-\section{Discussion and Analysis}
+\subsection{Discussion and Analysis}
 \label{appraisal}
 
-xThe problem of
+The problem of
 a BBC-wide search application was predicted --
@@
 
-\chapter{Evaluation}
+\section{Evaluation}
 \label{evaluation}
@@
 \appendix
-\chapter{Proposal}
+\section{Proposal}
 

### 2014-02-06 paper.tex
Capitalised heading.
Abbreviated "figure" to "Fig." as advised by format guide.

@@
-\documentclass{llncs}
+\documentclass[oribibl]{llncs}
 
@@
 \title{Designing a Search for the BBC}
-\author{Ross Fenning}
-\institute{BBC}
+\author{Ross Fenning\inst{1}}
+\institute{BBC \email{Ross.Fenning@bbc.co.uk}}
 
@@
 
-\tableofcontents
+\begin{abstract}
+
+\end{abstract}
 
@@
 search application to drive the missing components within the holistic
-system depicted in figure~\ref{rich-picture}. Some subsystems already
+system depicted in Fig.~\ref{rich-picture}. Some subsystems already
 exist, e.g. for journalists to write news articles and publish them on the
@@
 
-\subsection{Use cases}
+\subsection{Use Cases}
 
-From the rich picture in figure~\ref{rich-picture}, we can attempt to
+From the rich picture in Fig.~\ref{rich-picture}, we can attempt to
 extract the activities that are clearly within the remit of a search
@@
 search application directly (and the actors involved in those activities),
-we can produce the use case UML diagram shown in figure~\ref{use-case}.
+we can produce the use case UML diagram shown in Fig.~\ref{use-case}.
 
@@
 information that ultimately ends up in the search indexes and
-figure~\ref{sequence-user} shows a sequence diagram defining a user
+Fig.~\ref{sequence-user} shows a sequence diagram defining a user
 interacting with the search system
 
-The key design decision in figure~\ref{sequence-producer} is the use of
+The key design decision in Fig.~\ref{sequence-producer} is the use of
 asynchronous messages only. A non-blocking set of interactions such as
@@
 
-Note in figure~\ref{sequence-user} that while the search indexes
+Note in Fig.~\ref{sequence-user} that while the search indexes
 will contain representations of content
@@
 push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
-Such a solution is depicted in figure~\ref{sequence-ajax}. Whilst
+Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
 this still requires just as many calls to backend services --
@@
 the search application could return as a search result. A maximal
-model is shown in figure~\ref{model} that attempts to capture
+model is shown in Fig.~\ref{model} that attempts to capture
 a good proportion of the content and concepts the BBC has
@@
 
-The behaviour of the query web application in figure~\ref{sequence-user}
+The behaviour of the query web application in Fig.~\ref{sequence-user}
 is defined with a hard line
@@
 to an end user. This makes the AJAX-based alternative approach
-in figure~\ref{sequence-ajax}
+in Fig.~\ref{sequence-ajax}
 less of a desirable option (would a user really be presented a list
@@
 These decisions relate to how the system would implement the data model
-in figure~\ref{model}. The onotology described is an aggregation
+in Fig.~\ref{model}. The onotology described is an aggregation
 of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
@@
 
-Thus the domain model given in figure~\ref{model} should only serve
+Thus the domain model given in Fig.~\ref{model} should only serve
 as a communication artefact that leads to further development of

### 2014-02-06 paper.tex
Added abstract; replaced "I" with "the authors"; and abbreviation "section" as "Sect." where appropriate.

@@
 \begin{abstract}
-
+This paper combines Soft Systems Methodology and UML modelling to design a
+high-level view of a search application that receives web content
+from a variety of BBC content production systems and makes every item
+then searchable by a BBC website visitor using the search feature.
 \end{abstract}
@@
 
-The purpose of this report is to start the high-level design -- and perhaps
+The purpose of this paper is to start the high-level design -- and perhaps
 look at the lower levels of one or two aspects -- of a search application
@@
 representation of what is known about the problem. Figure~\ref{rich-picture}
-shows what I know of the audience, search and most BBC online content areas.
+shows what the authors know of the audience, search and most BBC online content areas.
 Note that not all areas are covered and a strong emphasis is placed on TV
@@
 and has certainly shown itself -- to be a very large-scale problem, the
-full extent of which cannot be covered in this report. Thus it
+full extent of which cannot be covered in this paper. Thus it
 is reasonable to conclude that the problem is not yet solved
@@
 (efficacy, efficiency and effectiveness) \citep{checkland1990soft},
-which is only briefly touched on in my attempts to relate the
+which is only briefly touched on in the authors' attempts to relate the
 data model to the user's interaction with the system.
@@
 
-Even the models that are presented in this report do not paint the full
+Even the models that are presented in this paper do not paint the full
 picture, but it could be argued that it is not their purpose to do so.
-As stated at the end of section~\ref{appraisal}, the use case diagram
+As stated at the end of Sect.~\ref{appraisal}, the use case diagram
 provides a starting point that might be sufficient for an early
@@
 to changes. A similar approach would allow us to start with the smaller
-domain model also discussed in section~\ref{appraisal} and allow it to grow
+domain model also discussed in Sect.~\ref{appraisal} and allow it to grow
 to the necessary size to need -- i.e. we can defer the decision of ``how big
@@
 returning rich information in a single response versus an AJAX-driven
-approach (or some trade-off in between). Again, I would emphasise the
+approach (or some trade-off in between). Again, the authors would emphasise the
 communication aspect of UML modelling and argue that encouraging such debate

### 2014-02-12 paper.tex
Added changes as given by Huseyin.

@@
 \begin{abstract}
-This paper combines Soft Systems Methodology and UML modelling to design a
-high-level view of a search application that receives web content
-from a variety of BBC content production systems and makes every item
-then searchable by a BBC website visitor using the search feature.
+
+Whilst there are successful general web search engines such a Google that
+will find any piece of content, there is a perceived need for a specific
+search that makes better use of the internal knowledge the broadcasting
+industry (e.g. BBC) has about its own content. The British Broadcasting
+Corporation (BBC) is a public service broadcaster funded by the licence
+fee paid by United Kingdom households. This industry-based case study
+combines Soft Systems Methodology (SSM) and Unified Modelling Language
+(UML) to design a high-level view of a search application that receives
+web content from a variety of BBC content production systems and makes
+every item then searchable by a BBC website visitor using the search
+feature. The developers of such search applications can benefit from this
+specific industry-based case study that contextualised the problem space
+using SSM and developed UML models to solve the problem.
+
 \end{abstract}
@@
 
-The overall design objective will be to create an initial proposal for a
+Dogan and Henshaw\citep{dogan2010conceptual}
+showed how a ‘soft’ systems approach called Interactive
+Management can be adopted to capture the requirements and contextualise the
+problem space. This involved the process of transitioning from the soft systems
+results to a formal model (e.g. UML). This transition was enabled by dividing
+the actors in the rich pictures into meta-level and direct users of the system.
+Although this division was subjective and depended on the interpretation  and
+analysis of the rich pictures to provide a structure for the use case model,
+the rich pictures themselves were created through interactions with subject
+matter experts. The soft systems, and hence the Interactive Management results,
+provided the baseline information to derive a formal model including UML use
+case, sequence and domain models. The transitioning from ``soft'' to ``hard''
+systems can be set within the State of the Art including the requirements
+analysis and modelling as used in SSM, UML and Business Process Modelling.
+
+The overall design objective of this paper will be to create an initial
+proposal for a
 search application to drive the missing components within the holistic
@@
 and informative material such as GCSE Bitesize or any other
-learning resouces.
+learning resources.
 
 The sequence diagram for the producer (or any other content creator)
-indirectly getting their content into the search system demonsrates
+indirectly getting their content into the search system demonstrates
 the need for asynchronous messaging (and publish-subscribe), but
 the nuances of such a process are not comprehensively shown in
-this format. A better illutration for such a message-based integration
-system might be derived from the illutrated patterns created
+this format. A better illustration for such a message-based integration
+system might be derived from the illustrated patterns created
 by Hohpe and Woolf. \citep{hohpe2004enterprise}
@@
 The latter pattern fully decouples the search indexes from any
-deeper information -- leaving that responsbility to appropriate
+deeper information -- leaving that responsibility to appropriate
 source system -- but means that the raw, stub results are near-useless
@@
 These decisions relate to how the system would implement the data model
-in Fig.~\ref{model}. The onotology described is an aggregation
+in Fig.~\ref{model}. The ontology described is an aggregation
 of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
@@
 
-\appendix
-\section{Proposal}
-
-\input{proposal-contents}
+A post-analysis study is required to evaluate the SSM and UML models. The models
+need to be applied to further projects for validation and verification purposes.
+In addition, the maturity and evolution of the artefacts need to be considered
+e.g. adding, deleting, or modifying, if the boundary and context changes.
 

### 2014-02-12 paper.tex
Corrected citation.

@@
 
-\subsection{Objectives}
+\subsection{Objectives and Literative Review}
 
@@
 
-Dogan and Henshaw\citep{dogan2010conceptual}
+Dogan and Henshaw\citep{dogan2010transition}
 showed how a ‘soft’ systems approach called Interactive

### 2014-02-17 paper.tex
Further amendments as suggested and switched to the recommended bibliography style.

--- 2014-02-12 paper.tex
@@
-\documentclass[oribibl]{llncs}
+\documentclass{llncs}
 
@@
 \usepackage{url}
-\usepackage[square]{natbib}
+%\usepackage[square]{natbib}
 
-\title{Designing a Search for the BBC}
-\author{Ross Fenning\inst{1}}
-\institute{BBC \email{Ross.Fenning@bbc.co.uk}}
+\title{Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML}
+\author{Ross Fenning\inst{1}
+  \and Huseyin Dogan\inst{2}
+  \and Keith Phalp\inst{2}}
+\institute{BBC, UK \email{Ross.Fenning@bbc.co.uk}
+  \and Bournemouth University, UK \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
 
@@
 
-\subsection{Objectives}
+\subsection{Problem Space Contextualisation through Soft Systems}
 
@@
 Using \emph{Soft Systems Methodology} (SSM)
-\citep{checkland2006learning}, we can stand back from
+\cite{checkland2006learning}, we can stand back from
 an ontological approach of defining what the search system \emph{is} or
@@
 
-Checkland and Scoles \citep{checkland1990soft} decribed a \emph{Rich Picture} approach
+Checkland and Scoles\cite{checkland1990soft} decribed a \emph{Rich Picture} approach
 for representing a problem situation early in SSM approaches.
@@
 
-Dogan and Henshaw\citep{dogan2010conceptual}
+Dogan and Henshaw\cite{dogan2010transition}
 showed how a ‘soft’ systems approach called Interactive
@@
 
-It is likely that the design will look to integrate with
+The design will look to integrate with
 existing subsystems where possible rather than attempt to replicate
@@
 
-From the rich picture in Fig.~\ref{rich-picture}, we can attempt to
-extract the activities that are clearly within the remit of a search
+From the rich picture in Fig.~\ref{rich-picture}, we
+extracted the activities that are clearly within the remit of a search
 application. For example, the ability for editorial staff to manage
@@
 with the subsystem being designed. The \emph{systems thinking} approach
-advocated by Checkland \citep{checkland1999systems} encourages us to
+advocated by Checkland\cite{checkland1999systems} encourages us to
 consider the irreducible properties of each system at each level
@@
 asynchronous messages only. A non-blocking set of interactions such as
-publish-subscribe \citep{hohpe2004enterprise} is a good way to decouple
+publish-subscribe\cite{hohpe2004enterprise} is a good way to decouple
 systems that produce and store progamme information from the search
 application systems. If the systems surrounding the programmes database
-can be built a \emph{channel adapter} \citep{hohpe2004enterprise} to integrate
+can be built a \emph{channel adapter}\cite{hohpe2004enterprise} to integrate
 it to a messaging system, then the search indexes can receive changes to
@@
 about the domain model will not be held in the search indexes. This goes
-along with the principle of separation of concerns \citep{dijkstra1982role}
+along with the principle of separation of concerns\cite{dijkstra1982role}
 in that the search index component can focus on optimising its data
@@
 This can be seen as similar to the \emph{Lazy Load} pattern
-\citep{fowler2002patterns} in that the search indexes will only return
+\cite{fowler2002patterns} in that the search indexes will only return
 stub objects that are capable of retrieving the fuller information
@@
 One solution to this in modern web application design is to
-push the lazy loading into the web browser using AJAX. \citep{garrett2005ajax}
+push the lazy loading into the web browser using AJAX.\cite{garrett2005ajax}
 Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
@@
 information. Parts of the application might well want to incorporate
-a domain model \citep{fowler2002patterns} so as to understand how
+a domain model\cite{fowler2002patterns} so as to understand how
 to perform each of these actions against each possible item
-the search application could return as a search result. A maximal
-model is shown in Fig.~\ref{model} that attempts to capture
+the search application could return as a search result.
+
+Domains are the distinct subject matters present in any system
+representing large, reusable components and are depicted using a
+domain model which shows an organisation of UML packages and their
+dependencies.\cite{dickerson2009architecture} The use case diagram and domain model
+developed provides a baseline model for a future search application system.
+
+A maximal
+domain model is shown in Fig.~\ref{model} that attempts to capture
 a good proportion of the content and concepts the BBC has
-been attempting to model over several years. This model is
+been making efforts to model over several years. This model is
 an aggregate of individual ontologies developed for specific purposes,
@@
 
-Note that complexity of information for programmes alone. \citep{raimond2009bbc}
+Note that complexity of information for programmes alone.\cite{raimond2009bbc}
 A programme to a member of the public could actually refer to an
@@
 in general. An example of a brand would be
-\emph{Doctor Who}, which itself contains multiple series, which in turn
+\emph{Doctor Who},
+\footnote{\emph{Doctor Who} is a popular, long-running science-fiction
+television programme produced by the BBC and is frequently sought by users
+of the BBC iPlayer television catch-up service after an episode has aired.
+} which itself contains multiple series, which in turn
 contain a collection of episodes. Note that the brand itself has episodes
@@
 This leads to some difficult questions for a search application. If a user
-searches for the text ``doctor who'', are they expecting a link to the
+searches for the text ``doctor who'',
+are they expecting a link to the
 latest episode to watch on iPlayer, information about the next episode
@@
 
-The model also skims the surface of the sport ontology \citep{rayfield2011bbc}
+The model also skims the surface of the sport ontology\cite{rayfield2011bbc}
 created before the 2012 Olympic games, which aims to model the whole domain
@@
 very little has been touched on around users seeking educational
-and informative material such as GCSE Bitesize or any other
-learning resources.
+and informative material such as \emph{Bitesize}
+\footnote{\emph{Bitesize} is the name given to the BBC's free web-based
+study materials for school children aged between
+5 and 16, covering varying curricula for England, Wales and Scotland.}
+or any other learning resources.
 
@@
 system might be derived from the illustrated patterns created
-by Hohpe and Woolf. \citep{hohpe2004enterprise}
+by Hohpe and Woolf.\cite{hohpe2004enterprise}
 
@@
 At a basic level, this is not unlike a \emph{content enricher} pattern
-\citep{hohpe2004enterprise} whereby the search application
+\cite{hohpe2004enterprise} whereby the search application
 business layer enriches the stubs in the indexes with information
@@
 in Fig.~\ref{model}. The ontology described is an aggregation
-of several efforts by Raimond \citep{raimond2009bbc}, Rayfield
-\citep{rayfield2011bbc} and others -- along with some additional work
+of several efforts by Raimond\cite{raimond2009bbc}, Rayfield
+\cite{rayfield2011bbc} and others -- along with some additional work
 to join them together -- to represent the wealth of
@@
 without the burden of maintaining more than is necessary. The use
-of \emph{subtype polymorphism} \citep{booch2007object} is likely
+of \emph{subtype polymorphism}\cite{booch2007object} is likely
 to be key to ensure the search domain model contains only the APIs
@@
 The application could go further and interact via a single
-SearchResult \emph{facade} \citep{fowler2002patterns} whose
+SearchResult \emph{facade}\cite{fowler2002patterns} whose
 instances provide appropriate responses to canonical hooks
@@
 are likely to take in content from any number of future systems,
-there is an appeal to taking a schemaless approach \citep{sadalage2012nosql}
+there is an appeal to taking a schemaless approach\cite{sadalage2012nosql}
 and allow the search application's view layer to display
 different kinds of results differently via \emph{duck typing}.
-\citep{python2013ducktyping}
+\cite{python2013ducktyping}
 
@@
 implicit schema in the logic that creates these dynamic objects from
-source systems \citep{sadalage2012nosql} -- could prove to aid the
+source systems\cite{sadalage2012nosql} -- could prove to aid the
 search system's need to model different kinds of data in the same
@@
 application. The use cases are likely sufficient for early iterations
-or a \emph{Minimal Viable Product} \citep{junk2000dynamic} and
+or a \emph{Minimal Viable Product}\cite{junk2000dynamic} and
 the behaviours capture the overall needs of the system. There is still
@@
 Methodology to monitor the general model for Checkland's ``3 Es''
-(efficacy, efficiency and effectiveness) \citep{checkland1990soft},
+(efficacy, efficiency and effectiveness)\cite{checkland1990soft},
 which is only briefly touched on in the authors' attempts to relate the
@@
 provides a starting point that might be sufficient for an early
-iteration of a project in an \emph{Agile} methodology. \citep{beck2001agile}
+iteration of a project in an \emph{Agile} methodology.\cite{beck2001agile}
 
@@
 a lot of design decision at an early stage of a project -- a stage at which we arguably
-have the least information. \citep{kelly2013conway} However, there are plenty of
+have the least information.\cite{kelly2013conway} However, there are plenty of
 efforts in spite of this that promote modelling and UML being used
@@
 suggested as suitable in an Agile project.
-\citep{ambler2002agile} It may have been more suitable to incorporate
+\cite{ambler2002agile} It may have been more suitable to incorporate
 a more diverse range of modelling techniques in the design and analysis
@@
 
-\bibliographystyle{cell}
+\bibliographystyle{splncs}
 \bibliography{bibtex}

### 2014-02-17 paper.tex
Fixed typo.

@@
 
-Whilst there are successful general web search engines such a Google that
+Whilst there are successful general web search engines such as Google that
 will find any piece of content, there is a perceived need for a specific

### 2014-02-24 paper.tex
Moved full stops to right of citations where they occur at the end of sentences.

@@
 
-The purpose of this paper is to start the high-level design -- and perhaps
+The purpose of this paper is to start the high-level design -- and
 look at the lower levels of one or two aspects -- of a search application
@@
 One solution to this in modern web application design is to
-push the lazy loading into the web browser using AJAX.\cite{garrett2005ajax}
+push the lazy loading into the web browser using AJAX\cite{garrett2005ajax}.
 Such a solution is depicted in Fig.~\ref{sequence-ajax}. Whilst
@@
 domain model which shows an organisation of UML packages and their
-dependencies.\cite{dickerson2009architecture} The use case diagram and domain model
+dependencies\cite{dickerson2009architecture}. The use case diagram and domain model
 developed provides a baseline model for a future search application system.
@@
 
-Note that complexity of information for programmes alone.\cite{raimond2009bbc}
+Note that complexity of information for programmes alone\cite{raimond2009bbc}.
 A programme to a member of the public could actually refer to an
@@
 system might be derived from the illustrated patterns created
-by Hohpe and Woolf.\cite{hohpe2004enterprise}
+by Hohpe and Woolf\cite{hohpe2004enterprise}.
 
@@
 and allow the search application's view layer to display
-different kinds of results differently via \emph{duck typing}.
-\cite{python2013ducktyping}
+different kinds of results differently via \emph{duck typing}
+\cite{python2013ducktyping}.
 
@@
 provides a starting point that might be sufficient for an early
-iteration of a project in an \emph{Agile} methodology.\cite{beck2001agile}
+iteration of a project in an \emph{Agile} methodology\cite{beck2001agile}.
 
@@
 a lot of design decision at an early stage of a project -- a stage at which we arguably
-have the least information.\cite{kelly2013conway} However, there are plenty of
+have the least information\cite{kelly2013conway}. However, there are plenty of
 efforts in spite of this that promote modelling and UML being used
@@
 Rational Unified Process (RUP) and Agile Unified Process (AUP) have been
-suggested as suitable in an Agile project.
-\cite{ambler2002agile} It may have been more suitable to incorporate
+suggested as suitable in an Agile project\cite{ambler2002agile}.
+ It may have been more suitable to incorporate
 a more diverse range of modelling techniques in the design and analysis

### 2014-02-24 paper.tex
Reworded in small ways to keep up an emphasis on this being a hypothetical design approach.

@@
 fee paid by United Kingdom households. This industry-based case study
-combines Soft Systems Methodology (SSM) and Unified Modelling Language
-(UML) to design a high-level view of a search application that receives
+looks at the applicability of Soft Systems Methodology (SSM) and
+Unified Modelling Language (UML) to design a hypothetical, high-level
+view of a search application that receives
 web content from a variety of BBC content production systems and makes
@@
 
+Whilst the BBC website currently has a
+functional search feature already, this paper assumes building a new search application
+from the ground up so as to give full freedom to apply the analysis and design
+techniques therein. In practice, there are engineering challenges involved
+in maintaining and building on top of existing systems. Such challenges
+are out of scope for this paper.
+
 The target audience for the BBC is effectively the entire population of the UK
@@
 Dogan and Henshaw\cite{dogan2010transition}
-showed how a ‘soft’ systems approach called Interactive
+showed how a ``soft'' systems approach called Interactive
 Management can be adopted to capture the requirements and contextualise the
@@
 It has been expressed already that a BBC-wide search application
-is going to have to index, retrieve and display a diverse set of
+would need to index, retrieve and display a diverse set of
 information. Parts of the application might well want to incorporate
@@
 a significant amount of user research and requirements-gathering
-to collection all the possible use cases of the search system. It
+to collect all the possible use cases of the search system. It
 is likely that the variations of the use cases are so numerous
@@
 in this way is brittle with regard to changes therein. Duplication
-would only harm maintainability.
+of business models across different applications would only
+harm maintainability.
 
@@
 Thus even if the use case and domain models are not as comprehensive or
-as honed as they need to be to build the entire application, they serve
+as honed as they need to be to build an entire application, they serve
 their purpose adequately to communicate the first iterations of
@@
 
-The sequence diagrams seemed to provoke more debate of the merits of
+The sequence diagrams seem to provoke more debate of the merits of
 returning rich information in a single response versus an AJAX-driven
@@
 
-In conclusion, the UML modelling presented is a key part of solving
+In conclusion, the UML modelling presented communicates some promising
+approaches to
 the BBC search problem, but it is far from sufficient in its own right.

### 2014-02-24 paper.tex
Further emphasised the hypothetical nature, even changing the title.

@@
 
-\title{Designing a Search Application for the British Broadcasting Corporation (BBC) Using UML}
+\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
 \author{Ross Fenning\inst{1}
@@
 in maintaining and building on top of existing systems. Such challenges
-are out of scope for this paper.
+and details of the existing infrastructure are out of scope for this paper.
 

### 2014-03-31 paper.tex
Added some more detail around the goal of the paper based on peer review from submission to EMMSAD.

@@
 
-\subsection{Problem Space Contextualisation through Soft Systems}
-
-The purpose of this paper is to start the high-level design -- and
-look at the lower levels of one or two aspects -- of a search application
-specific to BBC content. The intent is to provide a consistent user interface
-that allows the audience to find news articles, sport results,
-TV catch-up, education resources and everything else the BBC produces.
+\subsection{Design Goals}
 
@@
 and details of the existing infrastructure are out of scope for this paper.
+
+The purpose of this paper is to explore how contextualisation through SSM
+and then using UML to form a high-level design might benefit building a
+hypothetical, new search application for the BBC.
+The hope is that insights from
+fresh analysis and design might form suitable proposals for potential
+improvements and development within the existing application.
+These approaches might also lead to further work to evaluate the
+current application by highlighting where the BBC Search application
+differs from an ``ideal'' model (if it can be described as such) derived from 
+such a redesign with a contemporary view of the problem space.
+
+Ultimately, any organisation like the BBC is unlikely to replace a large
+application atomically, but is likely to migrate over time to
+its ``ideal'' form with smaller, iterative improvements. It is proposed
+that there is some value in designing what that ``ideal'' form might
+be so as to provide proposals for those improvements.
+
+\subsection{Problem Space Contextualisation through Soft Systems}
 
@@
 differences are out of scope for this design.
+
+This rich picture was created using domain knowledge dervied from the existing
+search system and technical knowledge of the BBC websites. If the initial
+designs from this paper prove promising in practice, the authors would
+recommend repeating the exercise with a broader range of stakeholders
+and domain experts from respective subsystems. A rich picture does not
+have to serve as authoritative snapshot of the problem space, but can
+instead been seen as a collaborative exercise between stakeholders. Such
+contextualisation is likely worth iterating over time as the industry
+changes, e.g. the recent shift from separate mobile websites to
+\emph{Responsive Design}\cite{marcotte2010responsive} might change
+the understanding around mobile devices.
 
@@
 
+In other words, we can say
+that editorial staff and content editors might be seen as direct
+users of the system, with actors, presenters, etc. seen as meta-level
+users. This is justified by noting that journalists and editorial staff
+will have their content exactly as typed appear in search results, but
+production staff behind television and radio programming contribute
+only indirectly to the search system. They produce the content that users
+will later wish to see, but they have little contribution to the
+discovery of that content later on.
+
+This follows from the
+Interactive Management approach from Dogan and Henshaw\cite{dogan2010transition}
+and is still largely subjective. For example, if a journalist
+publishes to a content management system, with which a search
+system then integrates without their knowledge, can they still
+be considered to be a direct user of the search system? In this
+design we argue that such syndication into the search system means
+their actions (e.g. to publish, remove, update articles) will
+have direct effect on the search and discovery of those
+articles (e.g. they may become searchable, cease being searchable
+or start being searchable under new criteria) and thus they are
+direct users of the search system. It is recognised however, that
+a more collaborative rich picture drawn up with a wider set
+of stakeholders might lead to a different opinion.
+
 This is not to say that we can simply cross off certain elements from
@@
 
-Having extracted the activities that appear to pertain to the
-search application directly (and the actors involved in those activities),
-we can produce the use case UML diagram shown in Fig.~\ref{use-case}.
+Having extraced the direct users only of the search system, further
+requirements-gathering and business analysis can define their
+respective use cases of the system. An analysis based on domain
+knowledge from the existing search system leads to the
+use case UML diagram shown in Fig.~\ref{use-case}.
 
@@
 potential uses. For the purposes of our initial design, we can next look
-into defining the system behaviour for some of these use cases.
+into defining the system behaviour for some of these use cases. It should
+be noted that these are illustrative of the breadth of use cases, but
+deeper business analysis and creation of corresponding use cases
+(perhaps following the style of Cockburn\cite{cockburn2001writing})
+should be performed as part of a more in-depth study before the
+high-level design can be truly considered complete and valid.
 
@@
 
+The breadth of content the search system will need to index and retrieve
+sits across multiple systems within the BBC (e.g. programme metadata
+lives in a distinct location to news articles). The diversity of
+systems, formats and metadata involved suggested approaching the
+more functional design as a classic \emph{Enterprise Integration}
+problem\cite{brosey2001grand}.
+
 Figure~\ref{sequence-producer}
@@
 Fig.~\ref{sequence-user} shows a sequence diagram defining a user
-interacting with the search system
+interacting with the search system.
 

### 2014-06-02 talk.tex
Added headings to make up a basic outline.

\documentclass{beamer}

\usetheme{Pittsburgh}
\usecolortheme{beaver}

\usepackage{dot2texi}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{todonotes}

\mode<handout>{%
  \usepackage{pgfpages}
  \pgfpagesuselayout{resize to}[a4paper]
}

\title{Building a Web Search}
\author{Ross Fenning}
\institute{
  Senior Software Engineer
  \\Content Discovery
  \\Future Media
  \\BBC
}
\date{17 June, 2014}

\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

% Background
% Design Goals
% Contextualisation of the problems space through SSM
% Extracting use cases
% Designing behaviour for indirect users
% Designing behaviour for direct users
% Domain modelling for search -- model business rules as per benefits shown in background, but also keep it generic
% Discussion and Analysis -- Use cases - More SSM needed?
% Discussion and Analysis -- Domain Model -- Polymorphism
% Discussion and Analysis -- Domain Model -- Duck Typing
% Discussion -- More SSM: 3 Es?
% Shortcomings -- Performance? NFRs?
% Shortcomings -- Agile?
% Validation?

\end{document}

### 2014-06-05 talk.tex
First pass of the first section.
Made some headway into the use cases.

@@
 % Background
+\begin{frame}
+  \frametitle{About Me}
+  \begin{itemize}
+    \pause \item Senior Software Engineer
+    \pause \item BBC Future Media
+    \pause \item Content Discovery: Search
+    \pause \item BBC Academy and University of Bradford, UK
+    \pause \item Bournemouth University, UK and Lancaster University
+    \pause \item School of Design Engineering \& Computing at Bournemouth University
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{What is BBC Search?}
+  \framesubtitle{i.e. What do I work on?}
+  \includegraphics[width=\linewidth]{homepage.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Why BBC Search?}
+  \framesubtitle{Isn't Google good enough?}
+  \begin{itemize}
+    \pause \item We can search the BBC via Google
+    \pause \item What can the BBC offer that Google cannot?
+    \pause \item Domain knowledge about our own content
+    \pause \item More ``real time'' updates of content
+  \end{itemize}
+\end{frame}
+
 % Design Goals
+\begin{frame}
+  \frametitle{Design Goals}
+  \begin{itemize}
+    \pause \item Existing search application serves a wide variety of use cases
+    \pause \item Start high-level thinking and design of a new search application
+    \pause \item Take a ``fresh'' approach as if we are replacing the whole system
+    \pause \item A new design can (hopefully) inform iterative improvements on a current system
+    \pause \item Can SSM give us contextualisation that applies both to a new application and to existing systems?
+    \pause \item The Search application should integrate where possible with other existing systems
+    \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
+  \end{itemize}
+\end{frame}
+
 % Contextualisation of the problems space through SSM
+\begin{frame}
+  \frametitle{Problem Contextualisation through SSM}
+  \begin{itemize}
+    \pause \item Claim: ``Hard systems'' (e.g. UML) take an ontological view:
+    \begin{itemize}
+      \pause \item What components are there?
+      \pause \item Who are the actors?
+      \pause \item What are the interactions between actors and components?
+      \pause \item What are the computations or workflows steps/stages?
+    \end{itemize}
+    \pause \item Claim: SSM takes an epistemological view:
+    \begin{itemize}
+      \pause \item How does the holistic search system transform user needs to content and information?
+      \pause \item How can the purposeful activity be monitored?
+      \pause \item How is the activity observed by different observers?
+      \pause \item How can different observers inform the activity?
+    \end{itemize}
+    \pause \item Interactive Management (Dogan and Henshaw, 2010) can capture requirements and transition to formal models
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Problem Contextualisation through SSM}
+  \framesubtitle{Rich Picture}
+  \includegraphics[width=\linewidth]{rich-picture.png}
+\end{frame}
+
 % Extracting use cases
+\begin{frame}
+  \frametitle{Use Case Extraction}
+  \framesubtitle{Identifying users}
+  \begin{itemize}
+    \pause \item Identifier all users of the system in the rich picture
+    \pause \item Separate \emph{direct} users from \emph{meta-level} users
+    \pause \item Direct use cases should emerge from the rich picture
+    \pause \item This separation is still \emph{subjective} and use cases may change as the rich picture changes
+  \end{itemize}
+\end{frame}
+
 % Designing behaviour for indirect users
+\begin{frame}
+  \frametitle{Use Case Extraction}
+  \framesubtitle{Meta-level Users}
+  \begin{itemize}
+    \pause \item Meta-level users do not transition to the use case models directly
+    \pause \item \emph{Systems Thinking} tells us to consider how meta-level users are affected by emergent properties of the holistic system
+  \end{itemize}
+\end{frame}
+
 % Designing behaviour for direct users
+\begin{frame}
+  \frametitle{Use Case Extraction}
+  \framesubtitle{Direct Users}
+  \begin{itemize}
+    \pause \item Direct users transition directly to actors into a UML use case diagram
+    \pause \item Use cases should derive from and be justifiable by the rich picture
+    \pause \item Direct users divide up into \emph{content production} and \emph{audience}
+    \pause \item Examples of each:
+    \begin{itemize}
+      \pause \item Producers of TV programmes metadata
+      \pause \item Users of the search web application
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 % Domain modelling for search -- model business rules as per benefits shown in background, but also keep it generic

### 2014-06-10 talk.tex
Half way through the headings now.

@@
 
-\usetheme{Pittsburgh}
-\usecolortheme{beaver}
+\usetheme{Frankfurt}
+\usecolortheme{seagull}
 
@@
 
+\def\email#1{{\tt#1}}
+
 \mode<handout>{%
@@
 
-\title{Building a Web Search}
-\author{Ross Fenning}
-\institute{
-  Senior Software Engineer
-  \\Content Discovery
-  \\Future Media
-  \\BBC
-}
-\date{17 June, 2014}
+\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
+\author{Ross Fenning\inst{1}
+  \and Huseyin Dogan\inst{2}
+  \and Keith Phalp\inst{2}}
+\institute{BBC, UK \\ \email{Ross.Fenning@bbc.co.uk}
+  \and Bournemouth University, UK \\ \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
+\date{2014-06-17}
 
@@
     \pause \item A new design can (hopefully) inform iterative improvements on a current system
+    \pause \item The Search application should integrate where possible with other existing systems
     \pause \item Can SSM give us contextualisation that applies both to a new application and to existing systems?
-    \pause \item The Search application should integrate where possible with other existing systems
     \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
@@
   \framesubtitle{Rich Picture}
-  \includegraphics[width=\linewidth]{rich-picture.png}
+  \pause \includegraphics[width=\linewidth]{rich-picture.png}
 \end{frame}
@@
   \begin{itemize}
-    \pause \item Identifier all users of the system in the rich picture
+    \pause \item Identify all users of the system in the rich picture
     \pause \item Separate \emph{direct} users from \emph{meta-level} users
     \pause \item Direct use cases should emerge from the rich picture
-    \pause \item This separation is still \emph{subjective} and use cases may change as the rich picture changes
+    \pause \item NOTE: This separation is still \emph{subjective} and use cases may change as the rich picture changes
   \end{itemize}
@@
 
+\begin{frame}
+  \frametitle{Use Case Extraction}
+  \framesubtitle{UML Use Case Diagram}
+  \pause \includegraphics[width=\linewidth]{use_case.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{System Behaviour}
+  \framesubtitle{Programmes metadata producer}
+  \pause \includegraphics[width=\linewidth]{plant_sequence_producer.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{System Behaviour}
+  \framesubtitle{Website user}
+  \begin{center}
+    \pause \includegraphics[height=0.8\textheight]{plant_sequence_user.png}
+  \end{center}
+\end{frame}
+
+\begin{frame}
+  \frametitle{System Behaviour}
+  \framesubtitle{Lazy-loading page via AJAX}
+  \begin{center}
+    \pause \includegraphics[height=0.8\textheight]{plant_sequence_ajax.png}
+  \end{center}
+\end{frame}
+
 % Domain modelling for search -- model business rules as per benefits shown in background, but also keep it generic
+\begin{frame}
+  \frametitle{Domain Modelling}
+  \begin{itemize}
+    \pause \item Use cases identify types of content users want to search
+    \pause \item Ontology designs exist for specific content domains, e.g. programmes, sport
+    \pause \item A search across all content types needs a model to span all domains
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Domain Modelling}
+  \framesubtitle{Class Diagram}
+  \pause \includegraphics[width=\linewidth]{plant_model.png}
+\end{frame}
+
 % Discussion and Analysis -- Use cases - More SSM needed?

### 2014-06-10 talk.tex
First pass complete.

@@
   \frametitle{Design Goals}
+  \framesubtitle{Motivation}
   \begin{itemize}
-    \pause \item Existing search application serves a wide variety of use cases
     \pause \item Start high-level thinking and design of a new search application
@@
     \pause \item A new design can (hopefully) inform iterative improvements on a current system
+    \pause \item Existing search application serves a wide variety of use cases
     \pause \item The Search application should integrate where possible with other existing systems
-    \pause \item Can SSM give us contextualisation that applies both to a new application and to existing systems?
+    \pause \item Can SSM give us contextualisation so any modelling and design reflect the real world more appropriately?
     \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
+    \pause \item Can SSM ensure that the emergement properties of the whole meet the needs of the UK audience and people within the BBC?
   \end{itemize}
@@
 
-% Contextualisation of the problems space through SSM
+\begin{frame}
+  \frametitle{Design Goals}
+  \framesubtitle{Requirements}
+  \begin{itemize}
+    \pause \item Existing search application serves a wide variety of use cases
+    \pause \item The Search application should integrate where possible with other existing systems
+    \pause \item Website is very high traffic
+    \pause \item Different parts of the overall website are maintained by distinct teams
+    \pause \item Varying applications, data stores and content management systems
+  \end{itemize}
+\end{frame}
+
 \begin{frame}
@@
   \framesubtitle{Class Diagram}
-  \pause \includegraphics[width=\linewidth]{plant_model.png}
+  \begin{center}
+    \pause \includegraphics[height=0.8\textheight]{plant_model.png}
+  \end{center}
 \end{frame}
@@
 % Discussion and Analysis -- Use cases - More SSM needed?
+
+\begin{frame}
+  \frametitle{Discussion}
+  \framesubtitle{Use Cases}
+  \begin{itemize}
+    \pause \item Use case model seems justifiable at a high level
+    \pause \item Many use cases and variations are missing
+    \pause \item More collaborative and continuous use of SSM should incoporate respective domain experts
+    \pause \item More user testing, audience feedback, requirements-gathering, etc. needed
+    \pause \item Possible need to iterate SSM processes towards a collection of use case models
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Discussion}
+  \framesubtitle{System Behaviour}
+  \begin{itemize}
+    \pause \item Enterprise Integration patterns
+    \begin{itemize}
+      \pause \item Asynchronous messaging
+      \pause \item Content Enricher -- Replicate information from other systems redundantly
+      \pause \item Claim Check -- Store absolute minimum information to function and maintain references to source systems
+      \pause \item Index vs. warehouse?
+      \pause \item How to evaluate the better approach?
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 % Discussion and Analysis -- Domain Model -- Polymorphism
+\begin{frame}
+  \frametitle{Discussion}
+  \framesubtitle{Domain Model}
+  \begin{itemize}
+    \pause \item Large, fully-inclusive data model useful mainly as communication artefact
+    \pause \item Aggregate models hard to keep in sync with changes in respective domains
+    \pause \item We can extract a polymorphic supertype containing only properties needed for a search application
+    \pause \item We can go further and model a ``Search Result'' facade
+  \end{itemize}
+\end{frame}
+
 % Discussion and Analysis -- Domain Model -- Duck Typing
+\begin{frame}
+  \frametitle{Discussion}
+  \framesubtitle{Schemalessness and Duck Typing}
+  \begin{itemize}
+    \pause \item Statically typed approach: A \emph{Place} always has a ``today's weather forecast'' attribute
+    \pause \item Dynamically (``duck'') typed approach: any entity can have a ``today's weather forecast'' attribute and we display this forecast if that attribute is present
+    \pause \item Allows other entities in future to have forecasts too (e.g. \emph{Events} such as football matches)
+    \pause \item Search application can store all fields from upstream sources and choose when to start using them
+  \end{itemize}
+\end{frame}
+
 % Discussion -- More SSM: 3 Es?
+\begin{frame}
+  \frametitle{Discussion}
+  \framesubtitle{Overall Model}
+  \begin{itemize}
+    \pause \item Promising at a high level
+    \pause \item Agile methodology would encourage developing prototype or MVP to test assumptions early
+    \pause \item Lacking suitable ``monitoring'' of the system as taught by SSM, e.g. Checkland's ``3 Es'' (efficacy, efficiency, effectiveness)
+  \end{itemize}
+\end{frame}
+
 % Shortcomings -- Performance? NFRs?
+\begin{frame}
+  \frametitle{Evaluation and Difficulties}
+  \framesubtitle{Non-functional Requirements}
+  \begin{itemize}
+    \pause \item BBC is a high-traffic website
+    \pause \item Content such as news articles are published frequently
+    \pause \item How to model requirements around performance, robustness and latency?
+  \end{itemize}
+\end{frame}
+
 % Shortcomings -- Agile?
+\begin{frame}
+  \frametitle{Evaluation and Difficulties}
+  \framesubtitle{Detailed Design and Agile}
+  \begin{itemize}
+    \pause \item Models developed at such a high level lack detailed design (not surprisingly)
+    \pause \item Agile methodologies encourage designing and delivering a small part of the system early
+    \pause \item Detailed design emerges in response to feedback and change
+    \pause \item Hard models can be altered in time with these iterations
+    \pause \item We can defer outstanding questions about hard models until we might have more information
+    \pause \item This seems in line with the continuous feedback cycles within SSM
+  \end{itemize}
+\end{frame}
+
 % Validation?
 
+% Further Work
+\begin{frame}
+  \frametitle{Further Work}
+  \begin{itemize}
+    \pause \item How can the models be effectively validated?
+    \pause \item Can the rich picture and use of SSM be repeated and expanded with input from a wider range of experts?
+    \pause \item How will the models change when this happens?
+    \pause \item Are there more parallels between Agile and SSM that engineers in industry have yet to appreciate?
+    \pause \item Should more development processes be considered alongside SSM and UML? e.g. RUP (OpenUP) or AUP?
+  \end{itemize}
+\end{frame}
+
 \end{document}

### 2014-06-17 talk.tex
final version to be delivered

@@
     \pause \item BBC Academy and University of Bradford, UK
-    \pause \item Bournemouth University, UK and Lancaster University
+    \pause \item Bournemouth University and Lancaster University
     \pause \item School of Design Engineering \& Computing at Bournemouth University
@@
   \includegraphics[width=\linewidth]{homepage.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{BBC Search results}
+  \includegraphics[width=\linewidth]{results.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{BBC iPlayer Search results}
+  \includegraphics[width=\linewidth]{iplayer.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{CBBC Search results}
+  \includegraphics[width=\linewidth]{cbbc.png}
 \end{frame}
@@
   \begin{itemize}
-    \pause \item Start high-level thinking and design of a new search application
+    \pause \item Showcase possible modelling via high-level thinking and design of a new search application
     \pause \item Take a ``fresh'' approach as if we are replacing the whole system
     \pause \item A new design can (hopefully) inform iterative improvements on a current system
-    \pause \item Existing search application serves a wide variety of use cases
-    \pause \item The Search application should integrate where possible with other existing systems
     \pause \item Can SSM give us contextualisation so any modelling and design reflect the real world more appropriately?
-    \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
+    \pause \item Can SSM help us consider the holistic search system that emerges after this integration?
     \pause \item Can SSM ensure that the emergement properties of the whole meet the needs of the UK audience and people within the BBC?
@@
     \end{itemize}
-    \pause \item Interactive Management (Dogan and Henshaw, 2010) can capture requirements and transition to formal models
+    \pause \item Dogan and Henshaw (2010) showed a transtion from soft systems to hard models
   \end{itemize}
@@
 % Extracting use cases
-\begin{frame}
+\begin{frame}[fragile]
   \frametitle{Use Case Extraction}
   \framesubtitle{Identifying users}
+  \begin{center}
+    \begin{dot2tex}[dot,scale=0.6]
+      digraph G {
+        rankdir=LR;
+        node;
+        "Rich Picture" -> Users
+        Users -> "Direct Users";
+        Users -> "Indirect Users";
+      }
+      \end{dot2tex}
+    \quad
   \begin{itemize}
@@
   \end{itemize}
+    \end{center}
 \end{frame}
@@
     \pause \item Meta-level users do not transition to the use case models directly
-    \pause \item \emph{Systems Thinking} tells us to consider how meta-level users are affected by emergent properties of the holistic system
+    \pause \item We should still consider how meta-level users are affected by emergent properties of the holistic system
   \end{itemize}
@@
     \pause \item Many use cases and variations are missing
-    \pause \item More collaborative and continuous use of SSM should incoporate respective domain experts
+    \pause \item More collaborative and continuous use of SSM should incorporate respective domain experts
     \pause \item More user testing, audience feedback, requirements-gathering, etc. needed
@@
       \pause \item Asynchronous messaging
+      \pause \item Claim Check -- Store absolute minimum information to function and maintain references to source systems
       \pause \item Content Enricher -- Replicate information from other systems redundantly
-      \pause \item Claim Check -- Store absolute minimum information to function and maintain references to source systems
       \pause \item Index vs. warehouse?

### 2014-11-02 academy-talk.tex
Added talk to be given at the Academy course.

--- 2014-06-17 talk.tex
@@
 
-\usetheme{Frankfurt}
-\usecolortheme{seagull}
+\usetheme{Copenhagen}
+\usecolortheme{default}
 
@@
   \and Bournemouth University, UK \\ \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
-\date{2014-06-17}
+\date{2014-11-05}
 
@@
     \pause \item Senior Software Engineer
-    \pause \item BBC Future Media
-    \pause \item Content Discovery: Search
-    \pause \item BBC Academy and University of Bradford, UK
-    \pause \item Bournemouth University and Lancaster University
-    \pause \item School of Design Engineering \& Computing at Bournemouth University
+    \pause \item Future Media: Content Discovery: Search
   \end{itemize}
@@
   \includegraphics[width=\linewidth]{homepage.png}
-\end{frame}
-
-\begin{frame}
-  \frametitle{BBC Search results}
-  \includegraphics[width=\linewidth]{results.png}
-\end{frame}
-
-\begin{frame}
-  \frametitle{BBC iPlayer Search results}
-  \includegraphics[width=\linewidth]{iplayer.png}
-\end{frame}
-
-\begin{frame}
-  \frametitle{CBBC Search results}
-  \includegraphics[width=\linewidth]{cbbc.png}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Why BBC Search?}
-  \framesubtitle{Isn't Google good enough?}
-  \begin{itemize}
-    \pause \item We can search the BBC via Google
-    \pause \item What can the BBC offer that Google cannot?
-    \pause \item Domain knowledge about our own content
-    \pause \item More ``real time'' updates of content
-  \end{itemize}
 \end{frame}

### 2014-11-04 academy-talk.tex
Added book covers for SSM books.
Worked through about half of the slides.

@@
 \usepackage{todonotes}
+\usepackage{hyperref}
 
@@
   \begin{itemize}
-    \pause \item Showcase possible modelling via high-level thinking and design of a new search application
-    \pause \item Take a ``fresh'' approach as if we are replacing the whole system
-    \pause \item A new design can (hopefully) inform iterative improvements on a current system
-    \pause \item Can SSM give us contextualisation so any modelling and design reflect the real world more appropriately?
-    \pause \item Can SSM help us consider the holistic search system that emerges after this integration?
-    \pause \item Can SSM ensure that the emergement properties of the whole meet the needs of the UK audience and people within the BBC?
+    \item Showcase
+    \item Fresh approach
+    \item Inform improvements?
+    \item Contextualisation via SSM
+    \item Bring audience closer to the design
   \end{itemize}
@@
   \begin{itemize}
-    \pause \item Existing search application serves a wide variety of use cases
-    \pause \item The Search application should integrate where possible with other existing systems
-    \pause \item Website is very high traffic
-    \pause \item Different parts of the overall website are maintained by distinct teams
-    \pause \item Varying applications, data stores and content management systems
+    \item Existing search application serves a wide variety of use cases
+    \item The Search application should integrate where possible with other existing systems
+    \item Website is very high traffic
+    \item Different parts of the overall website are maintained by distinct teams
+    \item Varying applications, data stores and content management systems
   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{What is SSM?}
+  \framesubtitle{Peter Checkland}
+  \begin{center}
+    \includegraphics[height=0.8\textheight]{ssma.jpg}
+    \quad
+    \includegraphics[height=0.8\textheight]{stsp.jpg}
+  \end{center}
 \end{frame}
@@
   \begin{itemize}
-    \pause \item Claim: ``Hard systems'' (e.g. UML) take an ontological view:
+    \item Claim: ``Hard systems'' (e.g. UML) take an ontological view:
     \begin{itemize}
-      \pause \item What components are there?
-      \pause \item Who are the actors?
-      \pause \item What are the interactions between actors and components?
-      \pause \item What are the computations or workflows steps/stages?
+      \item What components are there?
+      \item Who are the actors?
+      \item What are the interactions between actors and components?
+      \item What are the computations or workflows steps/stages?
     \end{itemize}
@@
     \begin{itemize}
-      \pause \item How does the holistic search system transform user needs to content and information?
-      \pause \item How can the purposeful activity be monitored?
-      \pause \item How is the activity observed by different observers?
-      \pause \item How can different observers inform the activity?
+      \item How does the holistic search system transform user needs to content and information?
+      \item How can the purposeful activity be monitored?
+      \item How is the activity observed by different observers?
+      \item How can different observers inform the activity?
     \end{itemize}
@@
     \begin{itemize}
-    \pause \item Identify all users of the system in the rich picture
-    \pause \item Separate \emph{direct} users from \emph{meta-level} users
-    \pause \item Direct use cases should emerge from the rich picture
-    \pause \item NOTE: This separation is still \emph{subjective} and use cases may change as the rich picture changes
+    \item Identify all users
+    \item \emph{Direct} vs. \emph{meta-level} users
+    \item Direct use cases should emerge from the rich picture
+    \item Note that separation is \emph{subjective}
+    \item Use cases can change if rich picture changes
     \end{itemize}
@@
   \begin{itemize}
-    \pause \item Meta-level users do not transition to the use case models directly
-    \pause \item We should still consider how meta-level users are affected by emergent properties of the holistic system
+  \item Meta-level users do not transition to the use case models directly
+  \item We should still consider how meta-level users are affected by emergent properties of the holistic system
+    \begin{itemize}
+    \item Actors
+    \item Journalists
+    \item Parents
+    \item Other Future Media products?
+    \item Future Media staff
+    \end{itemize}
   \end{itemize}
@@
   \begin{itemize}
-    \pause \item Direct users transition directly to actors into a UML use case diagram
-    \pause \item Use cases should derive from and be justifiable by the rich picture
-    \pause \item Direct users divide up into \emph{content production} and \emph{audience}
-    \pause \item Examples of each:
+    \item Direct users transition directly to actors into a UML use case diagram
+    \item Use cases should derive from and be justifiable by the rich picture
+    \item Direct users divide up into \emph{content production} and \emph{audience}
+    \item Examples of each:
     \begin{itemize}
-      \pause \item Producers of TV programmes metadata
-      \pause \item Users of the search web application
+      \item News editors
+      \item Users of the search web application
     \end{itemize}
@@
   \framesubtitle{UML Use Case Diagram}
-  \pause \includegraphics[width=\linewidth]{use_case.png}
+  \includegraphics[width=\linewidth]{use_case.png}
 \end{frame}
@@
   \framesubtitle{Programmes metadata producer}
-  \pause \includegraphics[width=\linewidth]{plant_sequence_producer.png}
+  \includegraphics[width=\linewidth]{plant_sequence_producer.png}
 \end{frame}
@@
   \begin{center}
-    \pause \includegraphics[height=0.8\textheight]{plant_sequence_user.png}
+    \includegraphics[height=0.8\textheight]{plant_sequence_user.png}
   \end{center}
@@
   \begin{center}
-    \pause \includegraphics[height=0.8\textheight]{plant_sequence_ajax.png}
+    \includegraphics[height=0.8\textheight]{plant_sequence_ajax.png}
   \end{center}
@@
   \begin{itemize}
-    \pause \item Use cases identify types of content users want to search
-    \pause \item Ontology designs exist for specific content domains, e.g. programmes, sport
-    \pause \item A search across all content types needs a model to span all domains
+    \item Use cases identify types of content users want to search
+    \item Ontology designs exist for specific content domains, e.g. programmes, sport
+    \item A search across all content types needs a model to span all domains
   \end{itemize}
@@
   \begin{itemize}
-    \pause \item Use case model seems justifiable at a high level
-    \pause \item Many use cases and variations are missing
-    \pause \item More collaborative and continuous use of SSM should incorporate respective domain experts
-    \pause \item More user testing, audience feedback, requirements-gathering, etc. needed
-    \pause \item Possible need to iterate SSM processes towards a collection of use case models
+    \item Use case model seems justifiable at a high level
+    \item Many use cases and variations are missing
+    \item More collaborative and continuous use of SSM should incorporate respective domain experts
+    \item More user testing, audience feedback, requirements-gathering, etc. needed
+    \item Possible need to iterate SSM processes towards a collection of use case models
   \end{itemize}
@@
   \framesubtitle{System Behaviour}
+  \begin{columns}[T]
+
+    \column{0.5\textwidth}
+
+    \includegraphics[width=\linewidth]{eip.jpg}
+
+    \column{0.5\textwidth}
+
       \begin{itemize}
-    \pause \item Enterprise Integration patterns
-    \begin{itemize}
-      \pause \item Asynchronous messaging
-      \pause \item Claim Check -- Store absolute minimum information to function and maintain references to source systems
-      \pause \item Content Enricher -- Replicate information from other systems redundantly
-      \pause \item Index vs. warehouse?
-      \pause \item How to evaluate the better approach?
+      \item Asynchronous messaging
+      \item Claim Check
+      \item Content Enricher
+      \item Index vs. warehouse?
+      \item Objective evaluation?
       \end{itemize}
-  \end{itemize}
+
+  \end{columns}
 \end{frame}
@@
 
+\begin{frame}
+  \frametitle{Questions}
+  \begin{center}
+    \url{http://rossfenning.co.uk/pages/papers.html}\\
+    \texttt{Ross.Fenning@bbc.co.uk}\\
+    \texttt{@Avenger\_Penguin}
+  \end{center}
+\end{frame}
+
 \end{document}

### 2014-11-04 academy-talk.tex
Reviewed each slide at least once now.

@@
 
+%gets rid of bottom navigation bars
+\setbeamertemplate{footline}[frame number]{}
+
+%gets rid of navigation symbols
+\setbeamertemplate{navigation symbols}{}
+
 \begin{document}
@@
   \begin{itemize}
-    \pause \item Senior Software Engineer
-    \pause \item Future Media: Content Discovery: Search
+    \item Senior Software Engineer
+    \item Future Media: Content Discovery: Search
   \end{itemize}
@@
     \item Use cases identify types of content users want to search
+    \item Things we want to model should emerge from the rich picture
+    \item ``TV'' and ``Radio''? Or just ``programmes''?
     \item Ontology designs exist for specific content domains, e.g. programmes, sport
@@
   \frametitle{Domain Modelling}
-  \framesubtitle{Class Diagram}
+  \framesubtitle{Maximal Class Diagram/Domain Model}
   \begin{center}
@@
   \begin{itemize}
-    \pause \item Large, fully-inclusive data model useful mainly as communication artefact
-    \pause \item Aggregate models hard to keep in sync with changes in respective domains
-    \pause \item We can extract a polymorphic supertype containing only properties needed for a search application
-    \pause \item We can go further and model a ``Search Result'' facade
+    \item Large, maximal data model useful as communication artefact
+    \item Aggregate models hard to keep in sync with changes in respective domains
+    \item Does Search need to model all of this?
+      \begin{itemize}
+        \item Polymorphic supertype -- ``Thing'' class?
+        \item Facade -- ``SearchResult'' class?
+      \end{itemize}
   \end{itemize}
@@
   \begin{itemize}
-    \pause \item Statically typed approach: A \emph{Place} always has a ``today's weather forecast'' attribute
-    \pause \item Dynamically (``duck'') typed approach: any entity can have a ``today's weather forecast'' attribute and we display this forecast if that attribute is present
-    \pause \item Allows other entities in future to have forecasts too (e.g. \emph{Events} such as football matches)
-    \pause \item Search application can store all fields from upstream sources and choose when to start using them
+    \item Statically typed approach: A \emph{Place} always has a ``today's weather forecast'' attribute
+    \item Dynamically (``duck'') typed approach: any entity can have a ``today's weather forecast'' attribute and we display this forecast if that attribute is present
+    \item Allows other entities in future to have forecasts too (e.g. \emph{Events} such as football matches)
+    \item Search application can store all fields from upstream sources and choose when to start using them
   \end{itemize}
@@
   \frametitle{Discussion}
-  \framesubtitle{Overall Model}
+  \framesubtitle{Overall Model: Use cases, behaviour and domain}
   \begin{itemize}
-    \pause \item Promising at a high level
-    \pause \item Agile methodology would encourage developing prototype or MVP to test assumptions early
-    \pause \item Lacking suitable ``monitoring'' of the system as taught by SSM, e.g. Checkland's ``3 Es'' (efficacy, efficiency, effectiveness)
+    \item Looks good
+    \item Agile? MVP? Test assumptions?
+    \item How do we monitor for ``3 Es''?
+      \pause \begin{itemize}
+        \item Efficacy -- Does the system do what we intended?
+        \item Efficiency -- Does it minimise use of resources?
+        \item Effectiveness -- Does it fit into our long term goals?
+      \end{itemize}
+  \end{itemize}
+\end{frame}
+
+% Shortcomings -- Agile?
+\begin{frame}
+  \frametitle{Evaluation and Difficulties}
+  \framesubtitle{Detailed Design and Agile}
+  \begin{itemize}
+    \item High-level design lacks detail (not surprisingly)
+    \item Agile encourages delivering something tangible early
+    \item Shouldn't the full detailed design emerge iteratively?
+    \item Can we iteratively build up and maintain hard models?
+    \item Can we defer pending questions in our hard models until we know more?
+    \item SSM encourages continuous feedback cycles -- does this align with Agile?
+    \item Bustard, Dave, and Frank Keenan. ``Soft Systems Methodology: An Aid to Agile Development?.''
+      In \emph{Information Systems Development}, pp. 25-38. Springer US, 2009.
   \end{itemize}
@@
   \begin{itemize}
-    \pause \item BBC is a high-traffic website
-    \pause \item Content such as news articles are published frequently
-    \pause \item How to model requirements around performance, robustness and latency?
+    \item Performance
+    \item Availability/uptime
+    \item Latency between publishing and searchability
+    \item Secure/robust
+    \item Maintainability -- the holistic system includes developers!
   \end{itemize}
@@
 
-% Shortcomings -- Agile?
-\begin{frame}
-  \frametitle{Evaluation and Difficulties}
-  \framesubtitle{Detailed Design and Agile}
-  \begin{itemize}
-    \pause \item Models developed at such a high level lack detailed design (not surprisingly)
-    \pause \item Agile methodologies encourage designing and delivering a small part of the system early
-    \pause \item Detailed design emerges in response to feedback and change
-    \pause \item Hard models can be altered in time with these iterations
-    \pause \item We can defer outstanding questions about hard models until we might have more information
-    \pause \item This seems in line with the continuous feedback cycles within SSM
-  \end{itemize}
-\end{frame}
-
-% Validation?
-
-% Further Work
 \begin{frame}
@@
   \begin{itemize}
-    \pause \item How can the models be effectively validated?
-    \pause \item Can the rich picture and use of SSM be repeated and expanded with input from a wider range of experts?
-    \pause \item How will the models change when this happens?
-    \pause \item Are there more parallels between Agile and SSM that engineers in industry have yet to appreciate?
-    \pause \item Should more development processes be considered alongside SSM and UML? e.g. RUP (OpenUP) or AUP?
+    \item Can SSM take a more formal place in our processes?
+    \item Are there more parallels between Agile and SSM that engineers in industry have yet to appreciate?
+    \item Can we streamline modelling and design to fit an iterative process?
   \end{itemize}

### 2014-11-05 academy-talk.tex
Final draft for delivering.

@@
     \item Future Media: Content Discovery: Search
+    \item Presented at EMMSAD workshop as part of CAiSE 2014
+      \begin{itemize}
+        \item Exploring Modelling Methods for Systems Analysis and Design
+        \item 26th International Conference on Advanced Information Systems Engineering
+      \end{itemize}
   \end{itemize}
@@
     \item The Search application should integrate where possible with other existing systems
-    \item Website is very high traffic
-    \item Different parts of the overall website are maintained by distinct teams
+    \item BBC website is very high traffic
+    \item Different parts of the BBC website are maintained by distinct teams
     \item Varying applications, data stores and content management systems
@@
   \frametitle{What is SSM?}
-  \framesubtitle{Peter Checkland}
+  \framesubtitle{Framework for ``messy'' problems}
   \begin{center}
@@
   \begin{itemize}
-    \item Claim: ``Hard systems'' (e.g. UML) take an ontological view:
+    \pause \item Claim: ``Hard systems'' (e.g. UML) take an ontological view:
     \begin{itemize}
@@
   \begin{itemize}
-  \item Meta-level users do not transition to the use case models directly
+  \item Meta-level users do not transition to use cases directly
   \item We should still consider how meta-level users are affected by emergent properties of the holistic system
@@
   \begin{itemize}
-    \item Direct users transition directly to actors into a UML use case diagram
+    \item Direct users transition directly to actors in a UML use case diagram
     \item Use cases should derive from and be justifiable by the rich picture
@@
       \begin{itemize}
-        \item Polymorphic supertype -- ``Thing'' class?
+        \item Supertype -- ``Thing'' class?
         \item Facade -- ``SearchResult'' class?
@@
   \begin{itemize}
+    \item \url{http://martinfowler.com/articles/schemaless/}
     \item Statically typed approach: A \emph{Place} always has a ``today's weather forecast'' attribute
@@
     \item Search application can store all fields from upstream sources and choose when to start using them
+    \item Contextual validation enforces ``required'' fields are always populated
   \end{itemize}
@@
   \begin{itemize}
-    \item Looks good
+    \item Looks good\ldots at a high level
     \item Agile? MVP? Test assumptions?
@@
   \frametitle{Evaluation and Difficulties}
-  \framesubtitle{Detailed Design and Agile}
+  \framesubtitle{Detailed Design and Agile: Using SSM as part of BBC development practices?}
   \begin{itemize}
@@
     \item Can we iteratively build up and maintain hard models?
-    \item Can we defer pending questions in our hard models until we know more?
-    \item SSM encourages continuous feedback cycles -- does this align with Agile?
+    \item Can we defer questions in our hard models until we know more?
+    \item SSM encourages continuous feedback cycles -- Agile?
+    \item BDD encourages adding business context to features
     \item Bustard, Dave, and Frank Keenan. ``Soft Systems Methodology: An Aid to Agile Development?.''
